---
title: "Plant Growth Indices"
author: "S.Y. CHIA"
date: "January 16 2023"
output:
pdf_document: default
html_document: default
editor_options: null
  chunk_output_type: console
chunk_output_type: console
---


#1.0 Load required R libraries

```{r}

library(ggplot2)
library(car)
library(agricolae)
library(ggpubr)
library(emmeans)
library(multcompView)
library(plotrix) # for bar plots
library(lme4)
library(tidyverse)
library(RColorBrewer)
library(GGally)
library(lattice)
library(ggthemes)
library(DHARMa)
library(rmarkdown)
library(dgof)
library(moments)
library(glmmTMB)
library(dplyr)
library(multcomp)

```


#1.1 Set working directory


```{r}

setwd("C:/ATP_PROJECT/Data")


setwd("C:/ATP_PROJECT/Data")


```


#1.2 Load and prepare the data


```{r}

LA1<-read.table("Leafarea_trial_1.txt",header=TRUE)
LA2<-read.table("Leafarea_trial_2.txt",header=TRUE)
LN1<-read.table("Number_of_leaves_trial_1.txt",header=TRUE)
LN2<-read.table("Number_of_leaves_trial_2.txt",header=TRUE)
FT1<-read.table("flowering_time_trial_1.txt",header=TRUE)
FT2<-read.table("flowering_time_trial_2.txt",header=TRUE)

LA_N_incu<-read.table("IncubatedFrass_leafarea_leafcount.txt",header=TRUE)
LA_N_comp<-read.table("CompostedFrass_leafarea_leafcount.txt",header=TRUE)
FT_incu<-read.table("IncubatedFrass_floweringtime.txt",header=TRUE)
FT_comp<-read.table("CompostedFrass_floweringtime.txt",header=TRUE)


```


#1.3 Save data in appropriate format: 
## Set the variable characteristics correctly for LA1, LA2, LN1, LN2


```{r}

# Raw frass
LA1$amendment1 <- as.factor(LA1$amendment1)
LA1$time1 <- as.factor(LA1$time1) 
LA1$plant_id1 <- as.factor(LA1$plant_id1)
LA1$trial1 <- as.factor(LA1$trial1)
LA1$leafarea1 <- as.numeric(LA1$leafarea1)
LA1$leaflength1 <- as.numeric(LA1$leaflength1)
LA1$leafwidth1 <- as.numeric(LA1$leafwidth1)
	
LA2$amendment2 <- as.factor(LA2$amendment2)
LA2$time2 <- as.factor(LA2$time2) 
LA2$plant_id2 <- as.factor(LA2$plant_id2)
LA2$trial2 <- as.factor(LA2$trial2)
LA2$leafarea2 <- as.numeric(LA2$leafarea2)
LA2$leaflength2 <- as.numeric(LA2$leaflength2)
LA2$leafwidth2 <- as.numeric(LA2$leafwidth2)

LN1$amendment1 <- as.factor(LN1$amendment1)
LN1$time1 <- as.factor(LN1$time1)
LN1$trial1 <- as.factor(LN1$trial1) 
LN1$plant_id1 <- as.factor(LN1$plant_id1)
LN1$no_leaves1 <- as.numeric(LN1$no_leaves1)

LN2$amendment2 <- as.factor(LN2$amendment2)
LN2$time2 <- as.factor(LN2$time2)
LN2$trial2 <- as.factor(LN2$trial2) 
LN2$plant_id2 <- as.factor(LN2$plant_id2)
LN2$no_leaves2 <- as.numeric(LN2$no_leaves2)

FT1$amendment1 <- as.factor(FT1$amendment1)
FT1$trial1 <- as.factor(FT1$trial1) 
FT1$plant_id1 <- as.factor(FT1$plant_id1)
FT1$days_1 <- as.numeric(FT1$days_1)

FT2$amendment2 <- as.factor(FT2$amendment2)
FT2$trial2 <- as.factor(FT2$trial2) 
FT2$plant_id2 <- as.factor(FT2$plant_id2)
FT2$days_2 <- as.numeric(FT2$days_2)


# pre-treated (incubated and composted) frass
#LA_N_incu = Leaf Area and Number of leaves data
LA_N_incu$amendment<- as.factor(LA_N_incu$amendment)
LA_N_incu$time <- as.factor(LA_N_incu$time)
LA_N_incu$plant_id <-as.factor(LA_N_incu$plant_id)
LA_N_incu$leaf_count <-as.numeric(LA_N_incu$leaf_count)
LA_N_incu$leafarea <-as.numeric(LA_N_incu$leafarea)

LA_N_comp$amendment<- as.factor(LA_N_comp$amendment)
LA_N_comp$time <-as.factor(LA_N_comp$time)
LA_N_comp$plant_id<- as.factor(LA_N_comp$plant_id)
LA_N_comp$leaf_count<- as.numeric(LA_N_comp$leaf_count)
LA_N_comp$leafarea<- as.numeric(LA_N_comp$leafarea)

FT_incu$amendment<- as.factor(FT_incu$amendment)
FT_incu$days_incu<- as.numeric(FT_incu$days_incu)

FT_comp$amendment<- as.factor(FT_comp$amendment)
FT_comp$days_comp<- as.numeric(FT_comp$days_comp)


```


#1.4 Data structure and summary stats


```{r}

str(LA1)
summary(LA1)

str(LA2)
summary(LA2)

str(LN1)
summary(LN1)

str(LN2)
summary(LN2)

str(FT1)
summary(FT1)

str(FT2)
summary(FT2)

str(LA_N_incu)
summary(LA_N_incu)

str(LA_N_comp)
summary(LA_N_comp)


str(FT_incu)
summary(FT_incu)

str(FT_comp)
summary(FT_comp)


```


#1.5 Visualize data
## Leaf Area (LA)

Using boxplots, Q-Q Plots, bar graphs
'QQ Plot stands for Quantile vs Quantile Plot, which is exactly what it does: plotting theoretical quantiles against the actual quantiles of our variable'.
   
**sample sizes are very large (>30), therefore I ignore the test for normality**


```{r}

#leaf area and leaf count, raw frass
P <- ggplot(data = LA1, aes(x = amendment1, y = leafarea1))
    P + geom_boxplot()
    P + geom_col()
ggplot(data = LA1, aes(x = amendment1, y = leafarea1)) + geom_point()

qqnorm(LA1$leafarea1, pch = 1, frame = FALSE)
qqline(LA1$leafarea1, col = "steelblue", lwd = 2)


P1 <- ggplot(data = LA2, aes(x = amendment2, y = leafarea2))
    P1 + geom_boxplot()
    P1 + geom_col()
ggplot(data = LA2, aes(x = amendment2, y = leafarea2)) + geom_point()

qqnorm(LA2$leafarea2, pch = 1, frame = FALSE)
qqline(LA2$leafarea2, col = "steelblue", lwd = 2)


```


## Number of leaves (LN):

**sample sizes are very large (>30), therefore I ignore the test for normality**


```{r}

#leaf area and leaf count, raw frass
P2 <- ggplot(data = LN1, aes(x = amendment1, y = no_leaves1))
    P2 + geom_boxplot()
    P2 + geom_col()
ggplot(data = LN1, aes(x = amendment1, y = no_leaves1)) + geom_point()


P3 <- ggplot(data = LN2, aes(x = amendment2, y = no_leaves2))
    P3 + geom_boxplot()
    P3 + geom_col()

ggplot(data = LN1, aes(x = amendment1, y = no_leaves1)) + geom_point()
ggplot(data = LN2, aes(x = amendment2, y = no_leaves2)) + geom_point()

qqnorm(LN1$no_leaves1, pch = 1, frame = FALSE)
qqline(LN2$no_leaves2, col = "steelblue", lwd = 2)


#leaf area and leaf count, incubated frass
Pa3 <- ggplot(data = LA_N_incu, aes(x = amendment, y = leafarea))
    Pa3 + geom_boxplot()
    Pa3 + geom_col()
ggplot(data = LA_N_incu, aes(x = amendment, y = leafarea)) + geom_point()

Pb3 <- ggplot(data = LA_N_incu, aes(x = amendment, y = leaf_count))
    Pb3 + geom_boxplot()
    Pb3 + geom_col()
ggplot(data = LA_N_incu, aes(x = amendment, y = leaf_count)) + geom_point()


#leaf area and leaf count, composted frass
Pc3 <- ggplot(data = LA_N_comp, aes(x = amendment, y = leafarea))
    Pc3 + geom_boxplot()
    Pc3 + geom_col()
ggplot(data = LA_N_comp, aes(x = amendment, y = leafarea)) + geom_point()

Pd3 <- ggplot(data = LA_N_comp, aes(x = amendment, y = leaf_count))
    Pd3 + geom_boxplot()
    Pd3 + geom_col()
ggplot(data = LA_N_comp, aes(x = amendment, y = leaf_count)) + geom_point()


```


## Flowering time (FT):


```{r}

#flowering time, raw frass
P3a <- ggplot(data = FT1, aes(x = amendment1, y = days_1))
    P3a + geom_boxplot()
    P3a + geom_col()
ggplot(data = FT1, aes(x = amendment1, y = days_1)) + geom_point()


P3b <- ggplot(data = FT2, aes(x = amendment2, y = days_2))
    P3b + geom_boxplot()
    P3b + geom_col()
ggplot(data = FT2, aes(x = amendment2, y = days_2)) + geom_point()


#flowering time, processed frass (incubated and composted frass)
#Pd3 <- ggplot(data = FT_incu_comp, aes(x = amendment, y = Incubated))
    #Pd3 + geom_boxplot()
   # Pd3 + geom_col()
#ggplot(data = FT_incu_comp, aes(x = amendment, y = Incubated)) + geom_point()

#Pe3 <- ggplot(data = FT_incu_comp, aes(x = amendment, y = Composted))
    #Pe3 + geom_boxplot()
    #Pe3 + geom_col()
#ggplot(data = FT_incu_comp, aes(x = amendment, y = Composted)) + geom_point()


```


#1.6 Test for homogeneity of variance
##Leaf Area (LA)

**If the p-value for the 'Levene test' is greater than . 05, then the variances are not significantly different from each other (i.e., the homogeneity assumption of the variance is met).**

**If the p-value for the Levene's test is less than . 05, then there is a Significant difference between the variances.**


```{r}

leveneTest(leafarea1 ~ amendment1, data = LA1)
fligner.test(leafarea1 ~ amendment1, data = LA1)
bartlett.test(leafarea1 ~ amendment1, data = LA1) 

leveneTest(leafarea2 ~ amendment2, data = LA2)
fligner.test(leafarea2 ~ amendment2, data = LA2)
bartlett.test(leafarea2~ amendment2, data = LA2) 

```


## Number of leaves (LN)


```{r}

leveneTest(no_leaves1 ~ amendment1, data = LN1)
fligner.test(no_leaves1 ~ amendment1, data = LN1)
bartlett.test(no_leaves1 ~ amendment1, data = LN1)

leveneTest(no_leaves2 ~ amendment2, data = LN2)
fligner.test(no_leaves2 ~ amendment2, data = LN2)
bartlett.test(no_leaves2 ~ amendment2, data = LN2) 


```


#1.7 Test for Normality of variances - Leaf Area, Number of leaves

**If the sample size is large enough (n > 30), we can ignore the distribution of the data and use parametric tests. The central limit theorem tells us that no matter what distribution things have, 
the sampling distribution tends to be normal if the sample is large enough (n > 30).

*Shapiro-Wilk test* (recommended by Ghasemi & Zahediasl, 2002, doi: 10.5812/ijem.3505). It provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores.

**If the p-value is less than or equal to the significance level, the decision is to reject the null hypothesis and conclude that your data do not follow a normal distribution**.


```{r}

#leaf area
shapiro.test(LA1$leafarea1)
shapiro.test(LA2$leafarea2)

#number of leaves
shapiro.test(LN1$no_leaves1)
shapiro.test(LN2$no_leaves2)


```


#1.8 Model seection


```{r}

#leaf area, raw frass
lmer.LA1 <- lmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LA1)
glmmTMB.LA1 <- glmmTMB(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LA1)
gamma.LA1 <- glmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LA1)
AIC(lmer.LA1, glmmTMB.LA1, gamma.LA1)

lmer.LA2 <- lmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LA2)
glmmTMB.LA2 <- glmmTMB(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LA2)
gamma.LA2 <- glmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LA2)
AIC(lmer.LA2, glmmTMB.LA2, gamma.LA2)

# leaf count, raw frass
lmer.LN1 <- lmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LN1)
glmmTMB.LN1 <- glmmTMB(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LN1)
gamma.LN1 <- glmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LN1)
AIC(lmer.LN1, glmmTMB.LN1, gamma.LN1)

lmer.LN2 <- lmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LN2)
glmmTMB.LN2 <- glmmTMB(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LN2)
gamma.LN2 <- glmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LN2)
AIC(lmer.LN2, glmmTMB.LN2, gamma.LN2)

#leaf area, processed frass
lmer.LA_N_incu <- lmer(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
glmmTMB.LA_N_incu <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
gamma.LA_N_incu <- glmer(leafarea ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_incu)
AIC(lmer.LA_N_incu, glmmTMB.LA_N_incu, gamma.LA_N_incu)

lmer.LA_N_comp <- lmer(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
glmmTMB.LA_N_comp <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
gamma.LA_N_comp  <- glmer(leafarea ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_comp)
AIC(lmer.LA_N_comp , glmmTMB.LA_N_comp, gamma.LA_N_comp)

#leaf count, processed frass
pois.LA_N_incuL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = poisson, data = LA_N_incu)
glmmTMB.LA_N_incuL <- glmmTMB(leaf_count ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
gamma.LA_N_incuL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_incu)
AIC(pois.LA_N_incuL, glmmTMB.LA_N_incuL, gamma.LA_N_incuL)

pois.LA_N_compL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = poisson, data = LA_N_comp)
glmmTMB.LA_N_compL <- glmmTMB(leaf_count ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
gamma.LA_N_compL <-glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_comp)
AIC(pois.LA_N_compL, glmmTMB.LA_N_compL, gamma.LA_N_compL)

# flowering time, raw frass
pois.FT1 <- glm(days_1 ~ amendment1, data = FT1, family = poisson)
pois.FT1 <- glm(days_1 ~ amendment1, data = FT1, family = poisson)

glm.FT1 <- glm(days_1 ~ amendment1, data = FT1)
gamma.FT1 <- glm(days_1 ~ amendment1, family = Gamma(link = "log"), data = FT1)
AIC(pois.FT1, glm.FT1, gamma.FT1)

pois.FT2 <- glm(days_2 ~ amendment2, data = FT2, family = poisson)
glm.FT2 <- glm(days_2 ~ amendment2, data = FT2)
gamma.FT2 <- glm(days_2 ~ amendment2, family = Gamma(link = "log"), data = FT2)
AIC(pois.FT2, glm.FT2, gamma.FT2)


#flowering time, processed frass
pois.FT_incu <- glm(days_incu ~ amendment, data = FT_incu, family = poisson)
gamma.FT_incu <- glm(days_incu ~ amendment, family = Gamma(link = "log"), data = FT_incu)
AIC(pois.FT_incu, gamma.FT_incu)

pois.FT_comp <- glm(days_comp ~ amendment, data = FT_comp, family = poisson)
gamma.FT_comp <- glm(days_comp ~ amendment, family = Gamma(link = "log"), data = FT_comp)
AIC(pois.FT_comp, gamma.FT_comp)


#check for model problems using the DHARMa package - no problems detected
simulationOutput <- simulateResiduals(fittedModel = pois.FT_incu)
plot(simulationOutput)

simulationOutputinc <- simulateResiduals(fittedModel = gamma.FT_incu)
plot(simulationOutputinc)

simulationOutput <- simulateResiduals(fittedModel = pois.FT_comp)
plot(simulationOutput)

simulationOutput <- simulateResiduals(fittedModel = gamma.FT_comp)
plot(simulationOutput)


```


#2.0 Data analysis - Leaf Area, Number of leaves, flowering time

**Fit a mixed model: amendment effect is fixed, time and plant_id are random and independent.**
**effect of soil amendment was significant on leaf area and number of leaves**


```{r}

gamma.LA1 <- glmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LA1)
Anova(gamma.LA1)

gamma.LA2 <- glmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LA2)
Anova(gamma.LA2)

gamma.LN1 <- glmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"), data = LN1)
Anova(gamma.LN1)

gamma.LN2 <- glmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LN2)
Anova(gamma.LN2)

pois.FT1 <- glm(days_1 ~ amendment1, data = FT1, family = poisson)
Anova(pois.FT1) # significant

pois.FT2 <- glm(days_2 ~ amendment2, data = FT2, family = poisson)
Anova(pois.FT2)

#Processed frass
glmmTMB.LA_N_incu <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
Anova(glmmTMB.LA_N_incu)

glmmTMB.LA_N_comp <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
Anova(glmmTMB.LA_N_comp)

gamma.LA_N_incuL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_incu)
Anova(gamma.LA_N_incuL)

glmmTMB.LA_N_compL <- glmmTMB(leaf_count ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
Anova(glmmTMB.LA_N_compL)

pois.FT_comp <- glm(days_comp ~ amendment, data = FT_comp, family = poisson)
Anova(pois.FT_comp)

pois.FT_incu <- glm(days_incu ~ amendment, data = FT_incu, family = poisson)
Anova(pois.FT_incu)


```


#3.0 Posthoc test

**Tukey test using the emmeans (estimated marginal means) package**


```{r}

#raw frass
HSD_test <- emmeans(ref_grid(gamma.LA1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(gamma.LA1, regrid = "response"), pairwise ~ amendment1) 

HSD_test <- emmeans(ref_grid(gamma.LA2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(gamma.LA2, regrid = "response"), pairwise ~ amendment2)

HSD_test <- emmeans(ref_grid(gamma.LN1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(gamma.LN1, regrid = "response"), pairwise ~ amendment1)

HSD_test <- emmeans(ref_grid(gamma.LN2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(gamma.LN2, regrid = "response"), pairwise ~ amendment2)

LSD_Test<- LSD.test(pois.FT1,"amendment1", p.adj = "bonferroni", group = FALSE) # LSD test
LSD_Test


#processed frass
HSD_test <- emmeans(ref_grid(glmmTMB.LA_N_incu, regrid = "response"), pairwise ~ amendment)
emmeans(ref_grid(glmmTMB.LA_N_incu, regrid = "response"), pairwise ~ amendment)

HSD_test <- emmeans(ref_grid(glmmTMB.LA_N_comp, regrid = "response"), pairwise ~ amendment)
emmeans(ref_grid(glmmTMB.LA_N_comp, regrid = "response"), pairwise ~ amendment)

HSD_test <- emmeans(ref_grid(gamma.LA_N_compL, regrid = "response"), pairwise ~ amendment)
emmeans(ref_grid(gamma.LA_N_compL, regrid = "response"), pairwise ~ amendment) 


```


#4.0 Plots for leafarea, Number of leaves


```{r, echo=TRUE, eval=TRUE}

P4 <- ggplot(LA1, aes(amendment1, leafarea1))+ 
  geom_boxplot(aes(fill = amendment1),show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6")) # Dark Sky Blue
P4 + ylim(0, 115)

ggsave("boxplot_P4.pdf", width = 5, height = 4, dpi = 1000)


P5 <- ggplot(LA2, aes(amendment2, leafarea2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6")) # Dark Sky Blue
P5 + ylim(0, 115)

ggsave("boxplot_P5.jpeg", width = 5, height = 4, dpi = 1000)


P6 <- ggplot(LN1, aes(amendment1, no_leaves1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P6 + ylim(0, 15)

ggsave("boxplot_P6.jpeg", width = 5, height = 4, dpi = 1000)


P7 <- ggplot(LN2, aes(amendment2, no_leaves2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P7 + ylim(0, 15)

ggsave("boxplot_P7.jpeg", width = 5, height = 4, dpi = 1000)


#### Flowering time, raw frass
P7a <- ggplot(FT1, aes(amendment1, days_1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + # repeating this line helps to make the "mean symbol appear pure white
  labs(x = "Treatment", y = "Flowering time (days)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P7a + ylim (0, 96)

ggsave("boxplot_P7a.jpeg", width = 5, height = 4, dpi = 1000)


P7b <- ggplot(FT2, aes(amendment2, days_2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + # repeating this line helps to make the "mean symbol appear pure white
  labs(x = "Treatment", y = "Flowering time (days)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P7b + ylim (0, 80)

ggsave("boxplot_P7b.jpeg", width = 5, height = 4, dpi = 1000)


#Processed frass - plots

P8a <- ggplot(LA_N_incu, aes(amendment, leafarea))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8a + ylim(0, 60)

ggsave("boxplot_P8a.jpeg", width = 5, height = 4, dpi = 1000) # figure 6A, INCUBATED FRASS

P8b <- ggplot(LA_N_comp, aes(amendment, leafarea))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8b + ylim(0, 60)

ggsave("boxplot_P8b.jpeg", width = 5, height = 4, dpi = 1000) # figure 6B, COMPOSTED FRASS


P8c <- ggplot(LA_N_incu, aes(amendment, leaf_count))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8c + ylim(0, 15)

ggsave("boxplot_P8c.jpeg", width = 5, height = 4, dpi = 1000)


P8d <- ggplot(LA_N_comp, aes(amendment, leaf_count))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8d + ylim(0, 16)

ggsave("boxplot_P8d.jpeg", width = 5, height = 4, dpi = 1000)


P8e <- ggplot(FT_incu, aes(amendment, days_incu))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Time until flowering (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8e + ylim(0, 60)

ggsave("boxplot_P8e.jpeg", width = 5, height = 4, dpi = 1000)


P8f <- ggplot(FT_comp, aes(amendment, days_comp))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Time until flowering (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8f + ylim(0, 60)

ggsave("boxplot_P8f.jpeg", width = 5, height = 4, dpi = 1000)


```


#5.0 NEW ANALYSES

##5.1 Raw Frass 1, Trial 1

###Leaf area1

By day 35 - 42, the negative effect of Mealworm frass had disappeared

#### Plots leafarea1, Trial 1, *separately*, i.e., for each time point (21,       28, 35 and 42 days since germination)


```{r}


# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)

# Filter data for the desired time1 values
filtered_LA1 <- subset(LA1, time1 %in% c(21, 28, 35, 42))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LA1 for the current time1 value
  subset_LA1 <- subset(filtered_LA1, time1 == time_val)
  
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA1$leafarea1)
  
  # Create the ggplot object
  plot <- ggplot(subset_LA1, aes(x = amendment1, y = leafarea1, fill = amendment1)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Leaf area (cm²)") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)

#########follow lines of code do  not respond, so are commented out!!!
# Calculate the mean values
# mean_values <- tapply(subset_LA1$leafarea1, subset_LA1$amendment1, mean)

# Plot the mean values as white squares
# points(mean_values, pch = 22, col = "red", bg = "white")


```


#### ALTERNATIVE 1,  not used 

This code works well: uses the R base plot; displays mean values as white squares, but whiskers are dash lined and capped with horizontal lines 



```{r}

# Filter data for the desired time1 values
filtered_LA1 <- subset(LA1, time1 %in% c(21, 28, 35, 42))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LA1 for the current time1 value
  subset_LA1 <- subset(filtered_LA1, time1 == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA1$leafarea1)
  
  # Create the boxplot
  
# Create the boxplot with filled (solid circles) dots for outliers
boxplot(leafarea1 ~ amendment1, data = subset_LA1,
        main = paste("Plant age =", time_val),
        lty = 1, 
        whisker.col = NA,
        xlab = "Treatment", ylab = "Leaf area (cm²)",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"),
        outpch = "\u25CF")# = "\u25CF" represents outpch = 20

# Calculate the mean values
mean_values <- tapply(subset_LA1$leafarea1, subset_LA1$amendment1, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


####ALTERNATIVE 2, not used 

Code below Works well: 
uses R base plot
displays mean values (white square)
but text appear dublicated on the y and x axes. 
However, this can be edited in 'pdf xchange' by remove the extra layer of text


```{r}


# Filter data for the desired time1 values
filtered_LA1 <- subset(LA1, time1 %in% c(21, 28, 35, 42))

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LA1 for the current time1 value
  subset_LA1 <- subset(filtered_LA1, time1 == time_val)

  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA1$leafarea1)

  # Create the boxplot with outline
  boxplot(leafarea1 ~ amendment1, data = subset_LA1,
          main = paste("Plant age =", time_val),
          whisklty = 1, whisklwd = 1.2,
          staplelty = 1, staplelwd = 1.2,
          boxlwd = 1.2, boxcol = "black",  # Add outline with black color
          ylim = c(y_min, y_max),
          col = "#91bad6", pch = 20,
          xlab = "Treatment", ylab = "Leaf area (cm²)")

  # Calculate the mean values
  mean_values <- tapply(subset_LA1$leafarea1, subset_LA1$amendment1, mean)

  # Plot the mean values as white squares without outline and caps
  for (i in seq_along(mean_values)) {
    treatment <- names(mean_values)[i]
    mean_val <- mean_values[i]
    x_coord <- match(treatment, unique(subset_LA1$amendment1))

    points(x = x_coord, y = mean_val, pch = 22, col = "white", bg = "white", cex = 1.5, lwd = 0)
  }

  # Set tick marks on the y-axis
  axis(2, at = pretty(subset_LA1$leafarea1), las = 1, col.axis = "black")

  # Add x-axis labels (treatment names)
  axis(1, at = seq_along(unique(subset_LA1$amendment1)), labels = levels(subset_LA1$amendment1),
       col.axis = "black", tick = FALSE)
}

# Remove extra margins around the plots
par(mar = c(3, 3, 1, 1))

# Add overall title to the composite plot
title("Composite Boxplot with Treatments and Outlines")


```


#### Plot leaf area at time points 21, 28 and 35 days, *Present as a panel*

(old code, not used)

```{r}

# Filter data for the desired time1 values
filtered_LA1 <- subset(LA1, time1 %in% c(21, 28, 35))

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35)) {
  # Subset LA1 for the current time1 value
  subset_LA1 <- subset(filtered_LA1, time1 == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA1$leafarea1)
  

# Create the boxplot
boxplot(leafarea1 ~ amendment1, data = subset_LA1,
        main = paste("Plant age =", time_val),
        lty = 1, whisker.col = NA,
        xlab = "Treatment", ylab = "Leaf area (sq cm)",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean values
mean_values <- tapply(subset_LA1$leafarea1, subset_LA1$amendment1, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


Plots for time points 42 (old code, not used)


```{r}

# Filter data for the desired time1 values
filtered_LA1 <- subset(LA1, time1 %in% c(42)) #

# Create separate boxplots for the time1 value = 42
for (time_val in c(42)) {
  # Subset LA1 for the current time1 value
  subset_LA1 <- subset(filtered_LA1, time1 == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA1$leafarea1)
  
# Create the boxplot
p_42 <- ggplot(subset_LA1, aes(amendment1, leafarea1))+ 
              geom_boxplot(aes(fill = amendment1), 
              whisker.col = NA,
              show.legend = FALSE) + 
              stat_summary(fun = mean, geom = "point", 
              col = "white", shape = 12) +
              stat_summary(fun = mean, geom = "point", 
              col = "white") +
              labs(title = paste("Plant age =", time_val),
              x = "Treatment", y = "Leaf area (sq cm)") +
              ylim(c(y_min, y_max)) +
              scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))}


```


#### Analysis (GLM) - Leafarea1


```{r}

# Subset the data for time1 = 21 and fit the GLM model
model_21 <- glm(leafarea1 ~ amendment1, data = subset(LA1, time1 == 21), family = gaussian)

# Print the ANOVA table for time1 = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)


# Subset the data for time1 = 28 and fit the GLM model
model_28 <- glm(leafarea1 ~ amendment1, data = subset(LA1, time1 == 28), family = gaussian)

# Print the ANOVA table for time1 = 28
anova_table_28 <- Anova(model_28)
print(anova_table_28)

# Subset the data for time1 = 35 and fit the GLM model
model_35 <- glm(leafarea1 ~ amendment1, data = subset(LA1, time1 == 35), family = gaussian)

# Print the ANOVA table for time1 = 35
anova_table_35<- Anova(model_35)
print(anova_table_35)

# Subset the data for time1 = 42 and fit the GLM model
model_42 <- glm(leafarea1 ~ amendment1, data = subset(LA1, time1 == 42), family = gaussian)

# Print the ANOVA table for time1 = 42
anova_table_42 <- Anova(model_42)
print(anova_table_42)


```


#### Post hoc test - leafarea1

```{r}

# You have already fitted the GLM models and stored them as 'model_21', 'model_28', 'model_35', 'model_42'

# Load the 'multcomp' package
library(multcomp)

# Create a data frame with the factor levels of 'amendment1'
amendment_levels <- levels(LA1$amendment1)

# Perform the Tukey post hoc test for time1 = 21
posthoc_21 <- glht(model_21, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 21
summary(posthoc_21, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 28
posthoc_28 <- glht(model_28, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 28
summary(posthoc_28, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 35
posthoc_35 <- glht(model_35, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 35
summary(posthoc_35, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 42
posthoc_42 <- glht(model_42, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 42
summary(posthoc_42, test = adjusted(type = "holm"), level = 0.05)


```


Count the number of samples for each time1 value, for each level of amendment1


```{r}

sample_counts <- table(LA1$time1, LA1$amendment1)

# Display the sample counts
print(sample_counts)


```


##5.2 Raw Frass 2, Trial 2

### Leaf area 2

By day 35 - 42, the negative effect of Mealworm frass had disappeared

#### Plots, separately, i.e., for each time point (21, 28, 35 and 42 days since germination).


```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)

# Filter data for the desired time2 values
filtered_LA2 <- subset(LA2, time2 %in% c(21, 28, 35, 42))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time2 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LA2 for the current time2 value
  subset_LA2 <- subset(filtered_LA2, time2 == time_val)
  
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA2$leafarea2)
  
  # Create the ggplot object
  plot <- ggplot(subset_LA2, aes(x = amendment2, y = leafarea2, fill = amendment2)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Leaf area (cm²)") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)


```


#####ALTERNATIVE, not used


```{r}

# Filter data for the desired time2 values
filtered_LA2 <- subset(LA2, time2 %in% c(21, 28, 35, 42))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time2 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LA2 for the current time2 value
  subset_LA2 <- subset(filtered_LA2, time2 == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA2$leafarea2)
  
  # Create the boxplot
  
# Create the boxplot
boxplot(leafarea2 ~ amendment2, data = subset_LA2,
        main = paste("Plant age =", time_val),
         lty = 1, whisker.col = NA,
        xlab = "Treatment", ylab = "Leaf area (sq cm)",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean values
mean_values <- tapply(subset_LA2$leafarea2, subset_LA2$amendment2, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


#### Analysis (GLM) - Leafarea2


```{r}

# Subset the data for time2 = 21 and fit the GLM model
model_21 <- glm(leafarea2 ~ amendment2, data = subset(LA2, time2 == 21), family = gaussian)

# Print the ANOVA table for time2 = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)


# Subset the data for time1 = 28 and fit the GLM model
model_28 <- glm(leafarea2 ~ amendment2, data = subset(LA2, time2 == 28), family = gaussian)

# Print the ANOVA table for time2 = 28
anova_table_28 <- Anova(model_28)
print(anova_table_28)

# Subset the data for time1 = 35 and fit the GLM model
model_35 <- glm(leafarea2 ~ amendment2, data = subset(LA2, time2 == 35), family = gaussian)

# Print the ANOVA table for time2 = 35
anova_table_35<- Anova(model_35)
print(anova_table_35)

# Subset the data for time2 = 42 and fit the GLM model
model_42 <- glm(leafarea2 ~ amendment2, data = subset(LA2, time2 == 42), family = gaussian)

# Print the ANOVA table for time2 = 42
anova_table_42 <- Anova(model_42)
print(anova_table_42)


```


Counts (replicates per treatment)


```{r}

sample_counts <- table(LA2$time2, LA2$amendment2)

# Display the sample counts
print(sample_counts)


```


#### Post hoc test - leafarea2


```{r}

# You have already fitted the GLM models and stored them as 'model_21', 'model_28', 'model_35', 'model_42'

# Load the 'multcomp' package
library(multcomp)

# Create a data frame with the factor levels of 'amendment2'
amendment_levels <- levels(LA2$amendment2)

# Perform the Tukey post hoc test for time2 = 21
posthoc_21 <- glht(model_21, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 21
summary(posthoc_21, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time2 = 28
posthoc_28 <- glht(model_28, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 28
summary(posthoc_28, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time2 = 35
posthoc_35 <- glht(model_35, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 35
summary(posthoc_35, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time2 = 42
posthoc_42 <- glht(model_42, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 42
summary(posthoc_42, test = adjusted(type = "holm"), level = 0.05)


```


##5.3 RawFrass 1, Trial 1

###Number of leaves1
Analyse leafnumber for each time point (21, 28, 35 and 42 days since germination).

#### Plots


```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)

# Filter data for the desired time1 values
filtered_LN1 <- subset(LN1, time1 %in% c(21, 28, 35, 42))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LN1 for the current time1 value
  subset_LN1 <- subset(filtered_LN1, time1 == time_val)
  
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LN1$no_leaves1)
  
  # Create the ggplot object
  plot <- ggplot(subset_LN1, aes(x = amendment1, y = no_leaves1, fill = amendment1)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Number of leaves") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)


```


#### ALTERNATIVE, not used


```{r}

# Filter data for the desired time1 values
filtered_LN1 <- subset(LN1, time1 %in% c(21, 28, 35, 42))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LA1 for the current time1 value
  subset_LN1 <- subset(filtered_LN1, time1 == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LN1$no_leaves1)
  
  # Create the boxplot
  
# Create the boxplot
boxplot(no_leaves1 ~ amendment1, data = subset_LN1,
        main = paste("Plant age =", time_val),
        xlab = "Treatment", ylab = "Number of leaves",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean value
mean_values <- tapply(subset_LN1$no_leaves1 , subset_LN1$amendment1, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


#### Analysis (GLM) - LeafNumber1


```{r}

# Subset the data for time1 = 21 and fit the GLM model
model_21 <- glm(no_leaves1 ~ amendment1, data = subset(LN1, time1 == 21), family = gaussian)

# Print the ANOVA table for time1 = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)


# Subset the data for time1 = 28 and fit the GLM model
model_28 <- glm(no_leaves1 ~ amendment1, data = subset(LN1, time1 == 28), family = gaussian)

# Print the ANOVA table for time1 = 28
anova_table_28 <- Anova(model_28)
print(anova_table_28)

# Subset the data for time1 = 35 and fit the GLM model
model_35 <- glm(no_leaves1 ~ amendment1, data = subset(LN1, time1 == 35), family = gaussian)

# Print the ANOVA table for time1 = 35
anova_table_35<- Anova(model_35)
print(anova_table_35)

# Subset the data for time1 = 42 and fit the GLM model
model_42 <- glm(no_leaves1 ~ amendment1, data = subset(LN1, time1 == 42), family = gaussian)

# Print the ANOVA table for time1 = 42
anova_table_42 <- Anova(model_42)
print(anova_table_42)


```


Count the number of samples for each time1 value, for each level of amendment1


```{r}

sample_counts <- table(LN1$time1, LN1$amendment1)

# Display the sample counts
print(sample_counts)


```


#### Post hoc test - Number of leaves, trial 1


```{r}

# You have already fitted the GLM models and stored them as 'model_21', 'model_28', 'model_35', 'model_42'

# Load the 'multcomp' package
library(multcomp)

# Create a data frame with the factor levels of 'amendment1'
amendment_levels <- levels(LN1$amendment1)

# Perform the Tukey post hoc test for time1 = 21
posthoc_21 <- glht(model_21, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 21
summary(posthoc_21, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 28
posthoc_28 <- glht(model_28, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 28
summary(posthoc_28, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 35
posthoc_35 <- glht(model_35, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 35
summary(posthoc_35, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 42
posthoc_42 <- glht(model_42, linfct = mcp(amendment1 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 42
summary(posthoc_42, test = adjusted(type = "holm"), level = 0.05)


```


##5.4 RawFrass 2, Trial 2

###Number of leaves2

#### Plots


```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)

# Filter data for the desired time1 values
filtered_LN2 <- subset(LN2, time2 %in% c(21, 28, 35, 42))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time1 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LN2 for the current time1 value
  subset_LN2 <- subset(filtered_LN2, time2 == time_val)
  
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LN2$no_leaves2)
  
  # Create the ggplot object
  plot <- ggplot(subset_LN2, aes(x = amendment2, y = no_leaves2, fill = amendment2)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Number of leaves") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)


```

#####ALTERNATIVE, not used

```{r}

# Filter data for the desired time2 values
filtered_LN2 <- subset(LN2, time2 %in% c(21, 28, 35, 42))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time2 value
for (time_val in c(21, 28, 35, 42)) {
  # Subset LN2 for the current time2 value
  subset_LN2 <- subset(filtered_LN2, time2 == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LN2$no_leaves2)
  
  # Create the boxplot
  
# Create the boxplot
boxplot(no_leaves2 ~ amendment2, data = subset_LN2,
        main = paste("Plant age =", time_val),
        lty = 1, whisker.col = NA,
        xlab = "Treatment", ylab = "Number of leaves",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean value
mean_values <- tapply(subset_LN2$no_leaves2 , subset_LN2$amendment2, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


#### Analysis (GLM) - *LeafNumber2* (Raw Frass)


```{r}

# Subset the data for time2 = 21 and fit the GLM model
model_21 <- glm(no_leaves2 ~ amendment2, data = subset(LN2, time2 == 21), family = gaussian)

# Print the ANOVA table for time2 = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)


# Subset the data for time2 = 28 and fit the GLM model
model_28 <- glm(no_leaves2 ~ amendment2, data = subset(LN2, time2 == 28), family = gaussian)

# Print the ANOVA table for time2 = 28
anova_table_28 <- Anova(model_28)
print(anova_table_28)

# Subset the data for time2 = 35 and fit the GLM model
model_35 <- glm(no_leaves2 ~ amendment2, data = subset(LN2, time2 == 35), family = gaussian)

# Print the ANOVA table for time2 = 35
anova_table_35<- Anova(model_35)
print(anova_table_35)

# Subset the data for time2 = 42 and fit the GLM model
model_42 <- glm(no_leaves2 ~ amendment2, data = subset(LN2, time2 == 42), family = gaussian)

# Print the ANOVA table for time2 = 42
anova_table_42 <- Anova(model_42)
print(anova_table_42)


```


Count the number of samples for each time2 value, for each level of amendment2


```{r}

sample_counts <- table(LN2$time2, LN2$amendment2)

# Display the sample counts
print(sample_counts)


```

#### Post hoc test - Number of leaves, trial 2

```{r}

# You have already fitted the GLM models and stored them as 'model_21', 'model_28', 'model_35', 'model_42'

# Load the 'multcomp' package
library(multcomp)

# Create a data frame with the factor levels of 'amendment2'
amendment_levels <- levels(LN2$amendment2)

# Perform the Tukey post hoc test for time2 = 21
posthoc_21 <- glht(model_21, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 21
summary(posthoc_21, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 28
posthoc_28 <- glht(model_28, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 28
summary(posthoc_28, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time1 = 35
posthoc_35 <- glht(model_35, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time2 = 35
summary(posthoc_35, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time2 = 42
posthoc_42 <- glht(model_42, linfct = mcp(amendment2 = "Tukey"))

# Print the Tukey post hoc test results for time1 = 42
summary(posthoc_42, test = adjusted(type = "holm"), level = 0.05)


```


##5.5 RawFrass 1, Trial 1

### Flowering time 1

#### Plot


```{r}
library(ggplot2)


P7a <- ggplot(FT1, aes(amendment1, days_1)) + 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) +
  labs(x = "Treatment", y = "Time until flowering (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6", "#91BAD6")) + # Dark Sky Blue
  ylim(0, 96) +
  theme(panel.grid = element_blank(),         # Remove gridlines
        panel.background = element_blank(),   # Remove background color
        panel.border = element_rect(color = "black", fill = NA))  # Add plot outline

print(P7a)


```

##5.6 RawFrass 2, Trial 2

###Flowering time 2

#### Plot


```{r}

library(ggplot2)

P7b <- ggplot(FT2, aes(amendment2, days_2)) + 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  labs(x = "Treatment", y = "Time until flowering (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6", "#91BAD6")) + # Dark Sky Blue
  ylim(0, 80) +
  theme(panel.grid = element_blank(),         # Remove gridlines
        panel.background = element_blank(),   # Remove background color
        panel.border = element_rect(color = "black", fill = NA))  # Add plot outline

print(P7b)


```

#### Make a composite plot of P7a and P7b

Make sure to install the package "patchwork"

install.packages("patchwork")


```{r}

# Load the required libraries
library(ggplot2)
library(patchwork)

# Combine the two plots using the `+` operator
composite_plot <- P7a + P7b

# Display the composite plot
print(composite_plot)


```


##5.7.1 Incubated frass

###Leaf area

####Plots Leafarea



```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)


# Filter data for the desired time2 values
filtered_LA_N_incu<- subset(LA_N_incu, time %in% c(14, 21, 28, 35))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  # Subset LA_N_incu for the current time value
  subset_LA_N_incu <- subset(filtered_LA_N_incu, time == time_val)
  
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_incu$leafarea)
  
  # Create the ggplot object
  plot <- ggplot(subset_LA_N_incu, aes(x = amendment, y = leafarea, fill = amendment)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Leaf area (cm²)") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)


```


####ALTERNATIVE, not used


```{r}

# Filter data for the desired time values
filtered_LA_N_incu<- subset(LA_N_incu, time %in% c(14, 21, 28, 35))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  # Subset LA_N_incu for the current time value
  subset_LA_N_incu <- subset(filtered_LA_N_incu, time == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_incu$leafarea)
  
  # Create the boxplot
  
boxplot(leafarea ~ amendment, data = subset_LA_N_incu,
        main = past--e("Plant age =", time_val),
        lty = 1, whisker.col = NA,
        xlab = "Treatment", ylab = "Leaf area (sq cm)",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean values
mean_values <- tapply(subset_LA_N_incu$leafarea, subset_LA_N_incu$amendment, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


#### Analysis (GLM)


```{r}

# Subset the data for time = 14 and fit the GLM model
model_14 <- glm(leafarea ~ amendment, data = subset(LA_N_incu, time == 14), family = gaussian)

# Print the ANOVA table for time = 14
anova_table_14 <- Anova(model_14)
print(anova_table_14)


# Subset the data for time = 21 and fit the GLM model
model_21<- glm(leafarea ~ amendment, data = subset(LA_N_incu, time == 21), family = gaussian)

# Print the ANOVA table for time = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)

# Subset the data for time = 28 and fit the GLM model
model_28 <- glm(leafarea ~ amendment, data = subset(LA_N_incu, time == 28), family = gaussian)

# Print the ANOVA table for time = 28
anova_table_28<- Anova(model_28)
print(anova_table_28)

# Subset the data for time = 35 and fit the GLM model
model_35 <- glm(leafarea ~ amendment, data = subset(LA_N_incu, time == 35), family = gaussian)

# Print the ANOVA table for time = 35
anova_table_35 <- Anova(model_35)
print(anova_table_35)


```


Counts (replicates per treatment)


```{r}

sample_counts <- table(LA_N_incu$time, LA_N_incu$amendment)

#Display the sample counts
print(sample_counts)


```


####Post hoc test


```{r}

# You have already fitted the GLM models and stored them as 'model_14', 'model_21', 'model_28', 'model_35'

# Load the 'multcomp' package
library(multcomp)

# Create a data frame with the factor levels of 'amendment2'
amendment_levels <- levels(LA_N_incu$amendment)


# Perform the Tukey post hoc test for time = 35
posthoc_35 <- glht(model_35, linfct = mcp(amendment = "Tukey"))

# Print the Tukey post hoc test results for time = 35
summary(posthoc_35, test = adjusted(type = "holm"), level = 0.05)


```


##5.7.2 Incubated frass

###Number of leaves

####Plots, Number of leaves


```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)


# Filter data for the desired time2 values
filtered_LA_N_incu <- subset(LA_N_incu, time %in% c(14, 21, 28, 35))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  # Subset LA_N_incu for the current time value
 subset_LA_N_incu <- subset(filtered_LA_N_incu, time == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
 y_max <- max(subset_LA_N_incu$leaf_count, na.rm = TRUE)
  
  # Create the ggplot object
  plot <- ggplot(subset_LA_N_incu, aes(x = amendment, y = leaf_count, fill = amendment)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Number of leaves") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)


```


####ALTERNATIVE, not used


```{r}

# Filter data for the desired time values
filtered_LA_N_incu<- subset(LA_N_incu, time %in% c(14, 21, 28, 35))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  
  # Subset LA_N_incu for the current time value
  subset_LA_N_incu <- subset(filtered_LA_N_incu, time == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_incu$leaf_count)
  
  # Create the boxplot
  
# Create the boxplot
boxplot(leaf_count ~ amendment, data = subset_LA_N_incu,
        main = paste("Plant age =", time_val),
        xlab = "Treatment", ylab = "Number of leaves",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean values
mean_values <- tapply(subset_LA_N_incu$leaf_count, subset_LA_N_incu$amendment, mean)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


####Analysis (GLM)

 No significant difference among amendments
 

```{r}

# Subset the data for time = 14 and fit the GLM model
model_14 <- glm(leaf_count ~ amendment, data = subset(LA_N_incu, time == 14), family = gaussian)

# Print the ANOVA table for time = 14
anova_table_14 <- Anova(model_14)
print(anova_table_14)


# Subset the data for time = 21 and fit the GLM model
model_21<- glm(leaf_count ~ amendment, data = subset(LA_N_incu, time == 21), family = gaussian)

# Print the ANOVA table for time = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)

# Subset the data for time = 28 and fit the GLM model
model_28 <- glm(leaf_count ~ amendment, data = subset(LA_N_incu, time == 28), family = gaussian)

# Print the ANOVA table for time = 28
anova_table_28<- Anova(model_28)
print(anova_table_28)

# Subset the data for time = 35 and fit the GLM model
model_35 <- glm(leaf_count ~ amendment, data = subset(LA_N_incu, time == 35), family = gaussian)

# Print the ANOVA table for time = 35
anova_table_35 <- Anova(model_35)
print(anova_table_35)


```


Counts (replicates per treatment)


```{r}

sample_counts <- table(LA_N_incu$time, LA_N_incu$amendment)

# Display the sample counts
print(sample_counts)


```


##5.7.3 Incubated frass

###Flowering time

####Plot, Flowering time


```{r}
library(ggplot2)

P8e <- ggplot(FT_incu, aes(amendment, days_incu)) + 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  labs(x = "Treatment", y = "Time until flowering (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6", "#91BAD6")) + # Dark Sky Blue
  ylim(0, 60) +
  theme(panel.grid = element_blank(),         # Remove gridlines
        panel.background = element_blank(),   # Remove background color
        panel.border = element_rect(color = "black", fill = NA))  # Add plot outline

print(P8e)



```


##5.8.1 Composted frass

###Leaf area

####Plots


```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)


# Filter data for the desired time2 values
filtered_LA_N_comp <- subset(LA_N_comp, time %in% c(14, 21, 28, 35))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  # Subset LA_N_incu for the current time value
 subset_LA_N_comp <- subset(filtered_LA_N_comp, time == time_val)
   
  
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_comp$leafarea)
  
  # Create the ggplot object
  plot <- ggplot(subset_LA_N_comp, aes(x = amendment, y = leafarea, fill = amendment)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Leaf area (cm²)") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      legend.position = "none",  # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),  # Remove major gridlines
      panel.grid.minor = element_blank(),  # Remove minor gridlines
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black")  # Add tick marks on the y-axis
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)


```


####ALTERNATIVE


```{r}

# Filter data for the desired time values
filtered_LA_N_comp <- subset(LA_N_comp, time %in% c(14, 21, 28, 35))

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  
  # Subset LA_N_comp for the current time value
  subset_LA_N_comp <- subset(filtered_LA_N_comp, time == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_comp$leafarea, na.rm = TRUE)
  
  # Create the boxplot
  boxplot(leafarea ~ amendment, data = subset_LA_N_comp,
          main = paste("Plant age =", time_val), 
          xlab = "Treatment", ylab = "Leaf area (sq cm)",
          ylim = c(y_min, y_max),
          col = c("#91bad6", "#91bad6", "#91bad6"))
  
  # Calculate the mean values
  mean_values <- tapply(subset_LA_N_comp$leafarea, subset_LA_N_comp$amendment, mean, na.rm = TRUE)
  
  # Plot the mean values as white squares
  points(mean_values, pch = 22, col = "white", bg = "white")}


```


####Analysis (GLM)


```{r}

# Subset the data for time = 14 and fit the GLM model
model_14 <- glm(leafarea ~ amendment, data = subset(LA_N_comp, time == 14), family = gaussian)

# Print the ANOVA table for time = 14
anova_table_14 <- Anova(model_14)
print(anova_table_14)


# Subset the data for time = 21 and fit the GLM model
model_21<- glm(leafarea ~ amendment, data = subset(LA_N_comp, time == 21), family = gaussian)

# Print the ANOVA table for time = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)

# Subset the data for time = 28 and fit the GLM model
model_28 <- glm(leafarea ~ amendment, data = subset(LA_N_comp, time == 28), family = gaussian)

# Print the ANOVA table for time = 28
anova_table_28 <- Anova(model_28)
print(anova_table_28)

# Subset the data for time = 35 and fit the GLM model
model_35 <- glm(leafarea ~ amendment, data = subset(LA_N_comp, time == 35), family = gaussian)

# Print the ANOVA table for time = 35
anova_table_35 <- Anova(model_35)
print(anova_table_35)


```


Count samples, while excluding NAs from the data


```{r}

# Exclude NA values from the dataset
filtered_LA_N_comp <- na.omit(LA_N_comp)

# Counts (replicates per treatment)
sample_counts <- table(filtered_LA_N_comp$time, filtered_LA_N_comp$amendment)

# Display the sample counts
print("Counts (replicates per treatment):")
print(sample_counts)

```


####Post hoc test: run codes for model_14 and model_35 separately


```{r}

# You have already fitted the GLM models and stored them as 'model_14'

# Load the necessary library (if not already loaded)
library(lsmeans)

# Perform the LSD post hoc test
posthoc_14 <- lsmeans(model_14, pairwise ~ amendment, adjust = "none")

# Print the LSD post hoc test results for time = 14
summary(posthoc_14, level = 0.05)


# Perform the LSD post hoc test
posthoc_35 <- lsmeans(model_35, pairwise ~ amendment, adjust = "none")

# Print the LSD post hoc test results for time = 
summary(posthoc_35, level = 0.05)


```


##5.8.2 Composted frass

###Number of leaves

####Plots 


```{r}

# code below is ok, 
# uses the *ggplot2* and *gridExtra* packages,
# but does not display mean values as white squares
# since adding mean values on boxplots is not a standard requirement,
# I will adopt this code.


# Load the required libraries
library(ggplot2)
library(gridExtra)

# Filter data for the desired time2 values
filtered_LA_N_comp <- subset(LA_N_comp, time %in% c(14, 21, 28, 35))

# Create a list to store the ggplot objects
plots_list <- list()

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  # Subset LA_N_comp for the current time value
  subset_LA_N_comp <- subset(filtered_LA_N_comp, time == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_comp$leaf_count, na.rm = TRUE)
  
  # Create the ggplot object
  plot <- ggplot(subset_LA_N_comp, aes(x = amendment, y = leaf_count, fill = amendment)) +
    geom_boxplot(width = 0.5, color = "black") + #add ',outlier.shape=NA' after "black" to exclude outliers
    # Boxplot aesthetics
    labs(title = paste("Plant age =", time_val), x = "Treatment", y = "Number of leaves") +
    ylim(y_min, y_max) +
    scale_fill_manual(values = c("#91bad6", "#91bad6", "#91bad6")) +
    theme_minimal() +
    theme(
      axis.text.x = element_text(angle = 0, hjust = 0.5),  # Do not rotate x-axis text
      axis.ticks.x = element_line(color = "black"),        # Add tick marks on the x-axis
      axis.ticks.y = element_line(color = "black"),        # Add tick marks on the y-axis
      legend.position = "none",                           # Remove the legend
      panel.border = element_rect(color = "black", fill = NA),  # Add panel borders
      panel.grid.major = element_blank(),                 # Remove major gridlines
      panel.grid.minor = element_blank()                  # Remove minor gridlines
    )
  
  # Append the plot to the list
  plots_list[[length(plots_list) + 1]] <- plot
}

# Arrange the plots in a grid layout (2 rows and 2 columns)
grid.arrange(grobs = plots_list, ncol = 2, nrow = 2)



```


####ALTERNATIVE, not used


```{r}

# Filter data for the desired time values
filtered_LA_N_comp<- subset(LA_N_comp, time %in% c(14, 21, 28, 35))

# Create a new empty plot
plot.new()

# Set the layout for the composite plot
par(mfrow = c(2, 2))  # 2 rows and 2 columns

# Create separate boxplots for each time value
for (time_val in c(14, 21, 28, 35)) {
  
  # Subset LA_N_incu for the current time value
  subset_LA_N_comp <- subset(filtered_LA_N_comp, time == time_val)
   
  # Determine the y-axis limits
  y_min <- 0
  y_max <- max(subset_LA_N_comp$leaf_count, na.rm = TRUE)
  
  
# Create the boxplot
boxplot(leaf_count ~ amendment, data = subset_LA_N_comp,
        main = paste("Plant age =", time_val),
        lty = 1, whisker.col = NA,
        xlab = "Treatment", ylab = "Number of leaves",
        ylim = c(y_min, y_max),
        col = c("#91bad6", "#91bad6", "#91bad6"))

# Calculate the mean values
mean_values <- tapply(subset_LA_N_comp$leaf_count, subset_LA_N_comp$amendment, mean, na.rm = TRUE)

# Plot the mean values as white squares
points(mean_values, pch = 22, col = "white", bg = "white")}


```


####Analysis (GLM)

 No significant difference among amendments
 

```{r}

# Subset the data for time = 14 and fit the GLM model
model_14 <- glm(leaf_count ~ amendment, data = subset(LA_N_comp, time == 14), family = gaussian)

# Print the ANOVA table for time = 14
anova_table_14 <- Anova(model_14)
print(anova_table_14)


# Subset the data for time = 21 and fit the GLM model
model_21<- glm(leaf_count ~ amendment, data = subset(LA_N_comp, time == 21), family = gaussian)

# Print the ANOVA table for time = 21
anova_table_21 <- Anova(model_21)
print(anova_table_21)

# Subset the data for time = 28 and fit the GLM model
model_28 <- glm(leaf_count ~ amendment, data = subset(LA_N_comp, time == 28), family = gaussian)

# Print the ANOVA table for time = 28
anova_table_28<- Anova(model_28)
print(anova_table_28)

# Subset the data for time = 35 and fit the GLM model
model_35 <- glm(leaf_count ~ amendment, data = subset(LA_N_comp, time == 35), family = gaussian)

# Print the ANOVA table for time = 35
anova_table_35 <- Anova(model_35)
print(anova_table_35)


```


Count samples, while excluding NAs from the data


```{r}

# Obtain summary statistics for the dataset, including NA counts
summary_stats <- summary(LA_N_comp, na.count = TRUE)

# Display the summary statistics
print(summary_stats)


```


####Post hoc test


```{r}

# You have already fitted the GLM models and stored them as 'model_14', 'model_21'

# Load the 'multcomp' package
library(multcomp)

# Create a data frame with the factor levels of 'amendment'
amendment_levels <- levels(LA_N_comp$amendment)


# Perform the Tukey post hoc test for time = 14
posthoc_14 <- glht(model_14, linfct = mcp(amendment = "Tukey"))

# Print the Tukey post hoc test results for time = 14
summary(posthoc_14, test = adjusted(type = "holm"), level = 0.05)

# Perform the Tukey post hoc test for time = 21
posthoc_21 <- glht(model_21, linfct = mcp(amendment = "Tukey"))

# Print the Tukey post hoc test results for time = 21
summary(posthoc_21, test = adjusted(type = "holm"), level = 0.05)


```


##5.8.3 Composted frass

###Flowering time

####Plot, Flowering time


```{r}

library(ggplot2)

P8f <- ggplot(FT_comp, aes(amendment, days_comp)) + 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  labs(x = "Treatment", y = "Time until flowering (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6", "#91BAD6")) + # Dark Sky Blue
  ylim(0, 60) +
  theme(panel.grid = element_blank(),         # Remove gridlines
        panel.background = element_blank(),   # Remove background color
        panel.border = element_rect(color = "black", fill = NA))  # Add plot outline

print(P8f)


```


#### Make a composite plot of P8e and P8f

Make sure to install the package "patchwork"

install.packages("patchwork")


```{r}

# Load the required libraries
library(ggplot2)
library(patchwork)

# Combine the two plots using the `+` operator
composite_plot <- P8e + P8f

# Display the composite plot
print(composite_plot)


```

