---
title: "Insect Herbivore Survival and Leaf damage": 
author: "S.Y. CHIA"
date: "January 17, 2023"
output:
pdf_document: default
html_document: default
     toc: true
     keep_md: true
editor_options: null
  chunk_output_type: console
chunk_output_type: console
---

# Load required R libraries


```{r Libraries}

library(ggplot2)
library(car)
library(agricolae)
library(ggpubr)
library(emmeans)
library(multcompView)
library(plotrix)
library(lme4)
library(tidyverse)
library(RColorBrewer)
library(GGally)
library(lattice)
library(ggthemes)
library(DHARMa)
library(rmarkdown)
library(dgof)
library(moments)
library(glmmTMB)
library(dplyr)
library(MASS)

```

# Set working directory

```{r}

```

# Load and prepare the data: *Delia radicum*

pupae recovered(DPR), pupal wet weight(DPW), fly emergence (DFE)

```{r}
DPR1<-read.table("delia_pupae_recovered_trial_1.txt",header=TRUE)
DPR2<-read.table("delia_pupae_recovered_trial_2.txt",header=TRUE)

DPW1<-read.table("delia_pupalweight_trial_1.txt",header=TRUE)
DPW2<-read.table("delia_pupalweight_trial_2.txt",header=TRUE)

DFE1<-read.table("delia_fly_emergence_trial_1.txt",header=TRUE)
DFE2<-read.table("delia_fly_emergence_trial_2.txt",header=TRUE)

```

# Save data in appropriate format - *Delia radicum*

  Set the variable characteristics correctly 					

```{r}
DPR1$amendment1 <- as.factor(DPR1$amendment1)
DPR1$trial1 <- as.factor(DPR1$trial1)
DPR1$plant_id1 <- as.factor(DPR1$plant_id1)
DPR1$larvae1 <- as.numeric(DPR1$larvae1)
DPR1$pupae1 <- as.numeric(DPR1$pupae1)
DPR1$tot_larv_pupa1 <- as.numeric(DPR1$tot_larv_pupa1)
DPR1$survival <- as.numeric(DPR1$survival)

DPR2$amendment2 <- as.factor(DPR2$amendment2)
DPR2$trial2 <- as.factor(DPR2$trial2)
DPR2$plant_id2 <- as.factor(DPR2$plant_id2)
DPR2$larvae2 <- as.numeric(DPR2$larvae2)
DPR2$pupae2 <- as.numeric(DPR2$pupae2)
DPR2$tot_larv_pupa2 <- as.numeric(DPR2$tot_larv_pupa2)
DPR2$survival <- as.numeric(DPR2$survival)

DPW1$amendment1 <- as.factor(DPW1$amendment1)
DPW1$trial1 <- as.factor(DPW1$trial1)
DPW1$sample1 <- as.factor(DPW1$sample1)
DPW1$pupalweight1 <- as.numeric(DPW1$pupalweight1)

DPW2$amendment2 <- as.factor(DPW2$amendment2)
DPW2$trial2 <- as.factor(DPW2$trial2)
DPW2$sample2 <- as.factor(DPW2$sample2)
DPW2$pupalweight2 <- as.numeric(DPW2$pupalweight2)

DFE1$amendment1 <- as.factor(DFE1$amendment1)
DFE1$trial1 <- as.factor(DFE1$trial1)
DFE1$days1 <- as.numeric(DFE1$days1)
DFE1$pupae1 <- as.numeric(DFE1$pupae1)
DFE1$flies1 <- as.numeric(DFE1$flies1)
DFE1$percent_per_day1 <- as.numeric(DFE1$percent_per_day1)

DFE2$amendment2 <- as.factor(DFE2$amendment2)
DFE2$trial2 <- as.factor(DFE2$trial2)
DFE2$days2 <- as.numeric(DFE2$days2)
DFE2$pupae2 <- as.numeric(DFE2$pupae2)
DFE2$flies2 <- as.numeric(DFE2$flies2)
DFE2$percent_per_day2 <- as.numeric(DFE2$percent_per_day2)

#save data frames as list
delia.list <- list("DPR1" =DPR1, 
                   "DPR2" =DPR2, 
                   "DPW1" =DPW1, 
                   "DPW2" =DPW2, 
                   "DFE1" =DFE1, 
                   "DFE2" =DFE2)

#change COLUMN NAMES
delia.list<-lapply(delia.list, function(x){
  colnames(x)[1]<-"amendment"
  return(x)
  })

#delia.list[1:2]<-lapply(delia.list[1:2], function(x){
  #colnames(x)[6]<-"tot_larv_pupa"
  #return(x)
  #})


delia.list[3:4]<-lapply(delia.list[3:4], function(x){ # 3:4 here represents objects 3 to 4 on the list of objects in delia.list. x = the whole data frame
  colnames(x)[4]<-"pupalweight" # 4 here represents column 4 on the data set
  return(x)
  })

delia.list[5:6]<-lapply(delia.list[5:6], function(x){
  colnames(x)[6]<-"percent_per_day"
  return(x)
  })

```

# Load and prepare the data: *Plutella xylostella*

  pupae recovered (PPR), leaf damage (PLD)

```{r}

PPR1<-read.table("plutella_pupae_recovered_trial_1.txt",header=TRUE)
PPR2<-read.table("plutella_pupae_recovered_trial_2.txt",header=TRUE)

PLD1<-read.table("plutella_leaf_damage_score_trial_1.txt",header=TRUE)
PLD2<-read.table("plutella_leaf_damage_score_trial_2.txt",header=TRUE)

```

# Save data in appropriate format

### *Plutella xylostella*

 Set the variable characteristics correctly

```{r}

PPR1$amendment1 <- as.factor(PPR1$amendment1)
PPR1$trial1 <- as.factor(PPR1$trial1)
PPR1$plant_id1 <- as.factor(PPR1$plant_id1)
PPR1$pupae1 <- as.numeric(PPR1$pupae1)
PPR1$survival <- as.numeric(PPR1$survival)

PPR2$amendment2 <- as.factor(PPR2$amendment2)
PPR2$trial2 <- as.factor(PPR2$trial2)
PPR2$plant_id2 <- as.factor(PPR2$plant_id2)
PPR2$pupae2 <- as.numeric(PPR2$pupae2)
PPR2$survival <- as.numeric(PPR2$survival)

PLD1$amendment1 <- as.factor(PLD1$amendment1)
PLD1$trial1 <- as.factor(PLD1$trial1)
PLD1$plant_id1 <- as.factor(PLD1$plant_id1)
PLD1$score1 <- as.numeric(PLD1$score1)

PLD2$amendment2 <- as.factor(PLD2$amendment2)
PLD2$trial2 <- as.factor(PLD2$trial2)
PLD2$plant_id2 <- as.factor(PLD2$plant_id2)
PLD2$score2 <- as.numeric(PLD2$score2)


#save data frames as list
plutella.list <- list("PPR1" =PPR1, 
                      "PPR2" =PPR2, 
                      "PLD1" =PLD1, 
                      "PLD2" =PLD2)


#change COLUMN NAMES
plutella.list <-lapply(plutella.list, function(x){
  colnames(x)[1]<-"amendment"# change name of column 1 heading in all data frames in this list
  return(x)
  })

#plutella.list[1:2]<-lapply(plutella.list[1:2], function(x){
  #colnames(x)[6]<-"pupae"
  #return(x)
  #})

plutella.list[3:4]<-lapply(plutella.list[3:4], function(x){
  colnames(x)[4]<-"score"
  return(x)
  })
                   

```

# View data structure and summary stats

**Median is greater than the Mean for DPR1, DPR2, DPW1, DPW2:** This means that the data are "skewed to the left"

```{r}

# Structure

str(DPR1) # Delia
str(DPR2)
str(DPW1)
str(DPW2)
str(DFE1)
str(DFE2)

str(PPR1) # Plutella
str(PPR2)
str(PLD1)
str(PLD2)

# Summary
lapply(delia.list,summary)
lapply(plutella.list,summary)

```

# Visualize data - *Delia radicum*

Use boxplots, Q-Q Plots, bar graphs 
'QQ Plot stands for Quantile vs Quantile Plot, which is exactly what it does: 
plotting theoretical quantiles against the actual quantiles of our variable'.
   
*sample sizes are very large (>30), therefore I ignore the test for normality*

```{r}

P8 <- ggplot(data = DPR1, aes(x = amendment1, y = survival))
    P8 + geom_boxplot()
    P8 + geom_col()
ggplot(data = DPR1, aes(x = amendment1, y = survival)) + geom_point()

qqnorm(DPR1$survival, pch = 1, frame = FALSE)
qqline(DPR1$survival, col = "steelblue", lwd = 2)


P9 <- ggplot(data = DPR2, aes(x = amendment2, y = survival))
    P9 + geom_boxplot()
    P9 + geom_col()
ggplot(data = DPR2, aes(x = amendment2, y = survival)) + geom_point()

qqnorm(DPR2$survival, pch = 1, frame = FALSE)
qqline(DPR2$survival, col = "steelblue", lwd = 2)


P10 <- ggplot(data = DPW1, aes(x = amendment1, y = pupalweight1))
    P10 + geom_boxplot()
    P10 + geom_col()
ggplot(data = DPW1, aes(x = amendment1, y = pupalweight1)) + geom_point()

qqnorm(DPW1$pupalweight1, pch = 1, frame = FALSE)
qqline(DPW1$pupalweight1, col = "steelblue", lwd = 2)


P11 <- ggplot(data = DPW2, aes(x = amendment2, y = pupalweight2))
    P11 + geom_boxplot()
    P11 + geom_col()
ggplot(data = DPW2, aes(x = amendment2, y = pupalweight2)) + geom_point()

qqnorm(DPW2$pupalweight2, pch = 1, frame = FALSE)
qqline(DPW2$pupalweight2, col = "steelblue", lwd = 2)


P12 <- ggplot(data = DFE1, aes(x = amendment1, y = percent_per_day1))
    P12 + geom_boxplot()
    P12 + geom_col()
ggplot(data = DFE1, aes(x = amendment1, y = percent_per_day1)) + geom_point()

qqnorm(DFE1$percent_per_day1, pch = 1, frame = FALSE)
qqline(DFE1$percent_per_day1, col = "steelblue", lwd = 2)


P13 <- ggplot(data = DFE2, aes(x = amendment2, y = percent_per_day2))
    P13 + geom_boxplot()
    P13 + geom_col()
ggplot(data = DFE2, aes(x = amendment2, y = percent_per_day2)) + geom_point()

qqnorm(DFE2$percent_per_day2, pch = 1, frame = FALSE)
qqline(DFE2$percent_per_day2, col = "steelblue", lwd = 2)


#ploting in lists
# lapply example: execute a funciton with multiple arguments on every slice of a list
plot_lp<-lapply(delia.list[1:2], function(part_of_list) # phrase "part-of-list" can be anything
 ggplot(data = part_of_list, aes(x = amendment, y = survival))+ geom_boxplot())
plot_lp

plot_lw<-lapply(delia.list[3:4], function(part_of_list)
 ggplot(data = part_of_list, aes(x = amendment, y = pupalweight))+ geom_boxplot())
plot_lw

plot_lf<-lapply(delia.list[5:6], function(part_of_list)
 ggplot(data = part_of_list, aes(x = amendment, y = percent_per_day))+ geom_boxplot())
plot_lf


```

# Visualize data - *Plutella xylostella*

Use boxplots, Q-Q Plots, bar graphs 
'QQ Plot stands for Quantile vs Quantile Plot, which is exactly what it does: plotting theoretical quantiles   against the actual quantiles of our variable'.
   
*sample sizes are very large (>30), therefore I ignore the test for normality*

```{r}

P14 <- ggplot(data = PPR1, aes(x = amendment1, y = survival))
    P14 + geom_boxplot()
    P14 + geom_col()
ggplot(data = PPR1, aes(x = amendment1, y = survival)) + geom_point()

qqnorm(PPR1$survival, pch = 1, frame = FALSE)
qqline(PPR1$survival, col = "steelblue", lwd = 2)


P15 <- ggplot(data = PPR2, aes(x = amendment2, y = survival))
    P15 + geom_boxplot()
    P15 + geom_col()
ggplot(data = PPR2, aes(x = amendment2, y = survival)) + geom_point()

qqnorm(PPR2$survival, pch = 1, frame = FALSE)
qqline(PPR2$survival, col = "steelblue", lwd = 2)


P16 <- ggplot(data = PLD1, aes(x = amendment1, y = score1))
    P16 + geom_boxplot()
    P16 + geom_col()
ggplot(data = PLD1, aes(x = amendment1, y = score1)) + geom_point()

qqnorm(PLD1$score1, pch = 1, frame = FALSE)
qqline(PLD1$score1, col = "steelblue", lwd = 2)


P17 <- ggplot(data = PLD2, aes(x = amendment2, y = score2))
    P17 + geom_boxplot()
    P17 + geom_col()
ggplot(data = PLD2, aes(x = amendment2, y = score2)) + geom_point()

qqnorm(PLD2$score2, pch = 1, frame = FALSE)
qqline(PLD2$score2, col = "steelblue", lwd = 2)


#ploting in lists
# lapply example: execute a funciton with multiple arguments on every slice of a list
plot_l_pup<-lapply(plutella.list[1:2], function(part_of_list) # phrase "part-of-list" can be anything
 ggplot(data = part_of_list, aes(x = amendment, y = survival))+ geom_boxplot())
plot_l_pup

plot_l_d<-lapply(plutella.list[3:4], function(part_of_list)
 ggplot(data = part_of_list, aes(x = amendment, y = score))+ geom_boxplot())
plot_l_d

```

# Test for homogeneity of variance - *Delia radicum*

**If the p-value for the 'Levene test' is greater than 0.05, then the variances are not significantly different from each other (i.e., the homogeneity assumption of the variance is met).**
**If the p-value for the Levene's test is less than . 05, then there is a Significant difference between the variances.**
**Pupae recovered and fly emergence data (trials 1 & 2) have homogeneous variances**
**Pupal weight data (trials 1 & 2) do NOT have homogeneous variances**
This is not considered here because GLM instead of ANOVA is applied**

```{r}

leveneTest(survival ~ amendment1, data = DPR1) # homogeneous
fligner.test(survival ~ amendment1, data = DPR1)
bartlett.test(survival ~ amendment1, data = DPR1) 

leveneTest(survival ~ amendment2, data = DPR2) # homogeneous
fligner.test(survival ~ amendment2, data = DPR2)
bartlett.test(survival~ amendment2, data = DPR2)

leveneTest(pupalweight1 ~ amendment1, data = DPW1) # not homogeneous
fligner.test(pupalweight1 ~ amendment1, data = DPW1)
bartlett.test(pupalweight1 ~ amendment1, data = DPW1) 

leveneTest(pupalweight2 ~ amendment2, data = DPW2) # not homogeneous
fligner.test(pupalweight2 ~ amendment2, data = DPW2)
bartlett.test(pupalweight2~ amendment2, data = DPW2)

leveneTest(percent_per_day1 ~ amendment1, data = DFE1) # homogeneous
fligner.test(percent_per_day1 ~ amendment1, data = DFE1)
bartlett.test(percent_per_day1 ~ amendment1, data = DFE1) 

leveneTest(percent_per_day2 ~ amendment2, data = DFE2) # homogeneous
fligner.test(percent_per_day2 ~ amendment2, data = DFE2)
bartlett.test(percent_per_day2 ~ amendment2, data = DFE2)

```

# Test for homogeneity of variance - *Plutella xylostella*

**If the p-value for the 'Levene test' is greater than . 05, then the variances are not significantly different from each other (i.e., the homogeneity assumption of the variance is met).**
**If the p-value for the Levene's test is less than 0.05, then there is a Significant difference between the variances.**

```{r}

leveneTest(survival ~ amendment1, data = PPR1)
fligner.test(survival ~ amendment1, data = PPR1)
bartlett.test(survival ~ amendment1, data = PPR1) 

leveneTest(survival ~ amendment2, data = PPR2)
fligner.test(survival ~ amendment2, data = PPR2)
bartlett.test(survival~ amendment2, data = PPR2)

leveneTest(score1 ~ amendment1, data = PLD1)
fligner.test(score1 ~ amendment1, data = PLD1)
bartlett.test(score1 ~ amendment1, data = PLD1) 

leveneTest(score2 ~ amendment2, data = PLD2)
fligner.test(score2 ~ amendment2, data = PLD2)
bartlett.test(score2~ amendment2, data = PLD2)

```

# Test for Normality of variances - *Delia radicum*

**If the sample size is large enough (n > 30), we can ignore the distribution of the data and use parametric tests.** **The central limit theorem tells us that no matter what distribution things have, the sampling distribution tends to be normal if the sample is large enough (n > 30)**

Shapiro-Wilk test **(recommended by Ghasemi & Zahediasl, 2002, doi: 10.5812/ijem.3505).** 
**It provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores.**

**If the p-value is less than or equal to the significance level, the decision is to reject the null hypothesis and conclude that your data do not follow a normal distribution.**

**Data are largely not normally distributed, hence I use the Generalized linear models instead of general linear models like ANOVA and linear regression models**

```{r}

shapiro.test(DPR1$survival) # not normally distributed
shapiro.test(DPR2$survival) # normally distributed, p>0.05

shapiro.test(DPW1$pupalweight1) # not normally distributed
shapiro.test(DPW2$pupalweight2) # not normally distributed

shapiro.test(DFE1$percent_per_day1) # not normally distributed
shapiro.test(DFE2$percent_per_day2) # not normally distributed

```

# Test for Normality of variances - *Plutella xylostella*

**Data are not normally distributed, hence I use the Generalized linear models instead of general linear models like ANOVA and linear regression models**
```{r}

shapiro.test(PPR1$survival) # normally distributed, p>0.05
shapiro.test(PPR2$survival) # normally distributed

shapiro.test(PLD1$score1) # not normally distributed, p<0.05
shapiro.test(PLD2$score2) # not normally distributed

```

#  Model seection - *Delia radicum*

```{r}

# Over dispersion function
Overdisp_fun <- function (model) {
	rdf <- df.residual(model)
	rp <- residuals(model, type = "pearson")
	Pearson.chisq <- sum(rp * rp)
	prat <- Pearson.chisq / rdf
	pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = F)
	c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
	}


pois.DPR1 <- glm(survival ~ amendment1, data = DPR1, family = poisson) 
qpois.DPR1 <- glm(survival ~ amendment1, data = DPR1, family = quasipoisson) # nbin.DPR1
glm.DPR1 <- glm(survival ~ amendment1, data = DPR1)
nbin.DPR1 <- glm.nb(survival ~ amendment1, data = DPR1)
AIC(pois.DPR1, qpois.DPR1, glm.DPR1, nbin.DPR1)
glm.nb

# Check over dispersion. The ratio should be around 1
Overdisp_fun(pois.DPR1)

pois.DPR2 <- glm(survival ~ amendment2, data = DPR2, family = poisson) # pois.DPR2	
qpois.DPR2 <- glm(survival ~ amendment2, data = DPR2, family = quasipoisson)
glm.DPR2 <- glm(survival ~ amendment2, data = DPR2)
nbin.DPR2 <- glm.nb(survival ~ amendment2, data = DPR2)
AIC(pois.DPR2, qpois.DPR2, glm.DPR2, nbin.DPR2)

Overdisp_fun(pois.DPR2)

gamma.DPW1 <- glm(pupalweight1 ~ amendment1, family = Gamma (link = "log"), data = DPW1)
glm.DPW1 <- glm(pupalweight1 ~ amendment1, data = DPW1) # glm.DPW1
AIC(gamma.DPW1, glm.DPW1)

gamma.DPW2 <- glm(pupalweight2 ~ amendment2, family = Gamma (link = "log"), data = DPW2)
glm.DPW2 <- glm(pupalweight2 ~ amendment2, data = DPW2) # glm.DPW2
AIC(gamma.DPW2, glm.DPW2)

#time to fly emergence (days)
pois.DFE1 <- glm(days1 ~ amendment1, data = DFE1, family = poisson) 
qpois.DFE1 <- glm(days1 ~ amendment1, data = DFE1, family = quasipoisson)
glm.DFE1 <- glm(days1 ~ amendment1, data = DFE1)
nbin.DFE1 <- glm.nb(days1 ~ amendment1, data = DFE1)
AIC(pois.DFE1, qpois.DFE1, glm.DFE1, nbin.DFE1)


pois.DFE2 <- glm(days2 ~ amendment2, data = DFE2, family = poisson) 
qpois.DFE2  <- glm(days2 ~ amendment2, data = DFE2, family = quasipoisson)
glm.DFE2  <- glm(days2 ~ amendment2, data = DFE2)
nbin.DFE2 <- glm.nb(days2 ~ amendment2, data = DFE2)
AIC(pois.DFE2, qpois.DFE2, glm.DFE2, nbin.DFE2)


```

# Data analysis - Delia radicum: larval survival, pupal weight

**Fit a mixed model: amendment effect is main/fixed and independent.**
**DPR1, DPR2, DPW1, show significant differences** *DPW2 is only marginally significant (p=0.077)*

```{r}

pois.DPR1 <- glm(survival ~ amendment1, data = DPR1, family = poisson)
Anova(pois.DPR1)

pois.DPR2 <- glm(survival ~ amendment2, data = DPR2, family = poisson)
Anova(pois.DPR2)

glm.DPW1 <- glm(pupalweight1 ~ amendment1, data = DPW1)
Anova(glm.DPW1)

glm.DPW2 <- glm(pupalweight2 ~ amendment2, data = DPW2)
Anova(glm.DPW2)

```

# Data analysis - Delia radicum: Fly emergence and time to emergence
 *compare 3 proportions using a chi-squared test*
 

```{r}

# Fly emergence
prop.test(x=c(32, 62, 50),n=c(40, 65, 57)) # trial 1

prop.test(x=c(22, 41, 35),n=c(29, 51, 45)) # trial 2


#time to emergence

pois.DFE1 <- glm(days1 ~ amendment1, data = DFE1, family = poisson) 
Anova(pois.DFE1) 

pois.DFE2  <- glm(days2 ~ amendment2, data = DFE2, family = poisson)
Anova(pois.DFE2)

```

# Performing analysis on lists (alternative method)

**lapply example: run a series of different functions on each slice of a list, for example using the output of one function as input to another. don't forget to define what is the object you want to return from the function**

```{r}
# since objects 1 and 2 use the same model, I use lapply to run both data sets at once
analysis_l<-lapply(delia.list[1:2], function(x){
glm_out <- glm(survival ~ amendment, data = x, family = poisson)
glm_out_anova<-Anova(glm_out) # defining output object
return(glm_out_anova)
})
analysis_l # "l" indicates list

```

# Marascuilo Procedure - Post hoc test

**Tukey test using the emmeans (estimated marginal means) package**
*DPR1, DPR2, DPW1, DFE1 (time)*

```{r}

HSD_test.pois.DPR1 <- emmeans(ref_grid(pois.DPR1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(pois.DPR1, regrid = "response"), pairwise ~ amendment1)

HSD_test.pois.DPR2 <- emmeans(ref_grid(pois.DPR2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(pois.DPR2, regrid = "response"), pairwise ~ amendment2)

#DPW1
HSD_test.DPW1 <- emmeans(ref_grid(glm.DPW1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(glm.DPW1, regrid = "response"), pairwise ~ amendment1)

#DFE1 (time to emergence)
HSD_test.lglm.DFE1 <- emmeans(ref_grid(lglm.DFE1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(lglm.DFE1, regrid = "response"), pairwise ~ amendment1)

#DFE1&2 (percent emergence)

# Comparing multiple proportions using The Marascuillo procedure
# A difference is statistically significant if its value exceeds the critical range value

# Trial 1
p = c(0.8000000, 0.9538462, 0.8771930) # Set the proportions of interest

N = length(p)
value = critical.range = c()

## Compute critical values.
for (i in 1:(N-1))
   { for (j in (i+1):N)
    {
     value = c(value,(abs(p[i]-p[j])))
     critical.range = c(critical.range,
      sqrt(qchisq(.95,2))*sqrt(p[i]*(1-p[i]) + p[j]*(1-p[j])))
    }
   }

round(cbind(value,critical.range),3) # 4 represents number of decimal places in the output


#Trial 2
p = c(0.7586207, 0.8039216, 0.7777778) 

N = length(p)
value = critical.range = c()

## Compute critical values.
for (i in 1:(N-1))
   { for (j in (i+1):N)
    {
     value = c(value,(abs(p[i]-p[j])))
     critical.range = c(critical.range,
      sqrt(qchisq(.95,2))*sqrt(p[i]*(1-p[i]) + p[j]*(1-p[j])))
    }
   }

round(cbind(value,critical.range),3)

```

# Plots for Delia radicum

```{r, echo=TRUE, eval=TRUE}

# Number of larvae + pupae retrieved (% survival)
P18 <- ggplot(DPR1, aes(amendment1, survival))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Percent survival of Delia radicum larvae")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P18 + ylim (0, 100)

ggsave("boxplot_P18.pdf", width = 5, height = 4, dpi = 1000) # P18 = Figure 3 in the manuscript
ggsave("boxplot_P18.SVG", width = 5, height = 4, dpi = 1000)


P19 <- ggplot(DPR2, aes(amendment2, survival))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Percent survival of Delia radicum larvae")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P19 + ylim (0, 100)

ggsave("boxplot_P19.pdf", width = 5, height = 4, dpi = 1000) 


# Pupal weight
P20 <- ggplot(DPW1, aes(amendment1, pupalweight1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Biomass (mg) of Delia radicum pupae")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P20 + ylim (0, 16)

ggsave("boxplot_P20.jpeg", width = 5, height = 4, dpi = 1000)# P19 = Figure 4 in the manuscript


P21 <- ggplot(DPW2, aes(amendment2, pupalweight2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Biomass (mg) of Delia radicum pupae")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P21 + ylim (0, 17)

ggsave("boxplot_P21.jpeg", width = 5, height = 4, dpi = 1000)


# Fly emergence
P22 <- ggplot(df_DFE1, aes(amendment1, percent_per_day1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Emergence of Delia radicum flies (%)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P22 + ylim (0, 80)

ggsave("boxplot_P22.jpeg", width = 5, height = 4, dpi = 1000)


P23 <- ggplot(df_DFE2, aes(amendment2, percent_per_day2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Emergence of Delia radicum flies (%)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P23 + ylim (0, 40)

ggsave("boxplot_P23.jpeg", width = 5, height = 4, dpi = 1000)

# Time to emergence
P24 <- ggplot(df_DFE1, aes(amendment1, days1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Time (days) to emergence of Delia radicum flies")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P24 + ylim (0, 15)

ggsave("boxplot_P24.jpeg", width = 5, height = 4, dpi = 1000)


P25 <- ggplot(df_DFE2, aes(amendment2, days2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Time (days) to emergence of Delia radicum flies")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P25 + ylim (0, 15)

ggsave("boxplot_P25.jpeg", width = 5, height = 4, dpi = 1000)



#lapply example: custom funcitons and lists

final_plot_function1<-function(df_input){
ggplot(df_input, aes(x = amendment, y = tot_larv_pupa))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Delia radicum (larvae + pupae) recovered per pot")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))+# Dark Sky Blue
  ylim (0, 10)
}

final_plot_function2<-function(df_input){
ggplot(df_input, aes(x = amendment, y = xxxxx))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Delia radicum (larvae + pupae) recovered per pot")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))+# Dark Sky Blue
  ylim (0, 10)
}

final_plot_function3<-function(df_input){
ggplot(df_input, aes(x = amendment, y = xxxxxx))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Delia radicum (larvae + pupae) recovered per pot")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))+# Dark Sky Blue
  ylim (0, 10)
}

#one by one
final_plot_function(df_input = delia.list$DPR1)
final_plot_function(df_input = delia.list$DPR2)

# with list
lapply(delia.list[1:2], final_plot_function)

```

#  Model seection - *Plutella xylostella*

```{r}

# Overdispersion function
Overdisp_fun <- function (model) {
	rdf <- df.residual(model)
	rp <- residuals(model, type = "pearson")
	Pearson.chisq <- sum(rp * rp)
	prat <- Pearson.chisq / rdf
	pval <- pchisq(Pearson.chisq, df = rdf, lower.tail = F)
	c(chisq = Pearson.chisq, ratio = prat, rdf = rdf, p = pval)
	}


qpois.PPR1 <- glm(survival ~ amendment1, family = quasipoisson, data = PPR1) # overdispersion
pois.PPR1 <- glm(survival ~ amendment1, family = poisson, data = PPR1)
glm.PPR1 <- glm(survival ~ amendment1, data = PPR1)
nbin.PPR1 <- glm.nb(survival ~ amendment1, data = PPR1)
AIC(qpois.PPR1, pois.PPR1, glm.PPR1, nbin.PPR1)

# Check overdispersion. The ratio should be around 1
Overdisp_fun(qpois.PPR1)

qpois.PPR2 <- glm(survival ~ amendment2, family = quasipoisson, data = PPR2) #overdispersion
pois.PPR2 <- glm(survival ~ amendment2, family = poisson, data = PPR2)
glm.PPR2 <- glm(survival ~ amendment2, data = PPR2)
nbin.PPR2 <- glm.nb(survival ~ amendment2, data = PPR2)
AIC(qpois.PPR2, pois.PPR2, glm.PPR2, nbin.PPR2)

Overdisp_fun(qpois.PPR2)


gamma.PLD1 <- glm(score1 ~ amendment1, family = Gamma(link = "log"), data = PLD1)
glm.PLD1 <- glm(score1 ~ amendment1, data = PLD1)
AIC(gamma.PLD1, glm.PLD1)


gamma.PLD2 <- glm(score2 ~ amendment2, family = Gamma(link = "log"), data = PLD2)
glm.PLD2 <- glm(score2 ~ amendment2, data = PLD2)
AIC(gamma.PLD2, glm.PLD2)

```

# Data analysis - Plutella xylostella

**Fit a mixed model: amendment effect is main/fixed and independent.**
*PLD1 is significan. when poisson odel is used*

```{r}

pois.PPR1 <- glm(survival ~ amendment1, family = poisson, data = PPR1)
Anova(pois.PPR1)

pois.PPR2 <- glm(survival ~ amendment2, family = poisson, data = PPR2)
Anova(pois.PPR2)

glm.PLD1 <- glm(score1 ~ amendment1, data = PLD1)
Anova(glm.PLD1)

glm.PLD2 <- glm(score2 ~ amendment2, data = PLD2)
Anova(glm.PLD2)


#list format
analysis_l_p<-lapply(plutella.list[1:2], function(xp){
pois.output <- glm(survival ~ amendment, family = poisson, data = xp) # xp can be anything
pois.output_anova<-Anova(pois.output)
return(pois.output_anova)
})
analysis_l_p

analysis_l_d<-lapply(plutella.list[3:4], function(xd){ # xd can be anything
glm.output <- glm(score ~ amendment, data = xd)
glm.output_anova<-Anova(glm.output)
return(glm.output_anova)
})
analysis_l_d


```

# Posthoc test - Plutella xylostella

```{r}

HSD_test <- emmeans(ref_grid(pois.PPR1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(pois.PPR1, regrid = "response"), pairwise ~ amendment1)

HSD_test <- emmeans(ref_grid(pois.PPR2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(pois.PPR2, regrid = "response"), pairwise ~ amendment2)

```

# Plots for Plutella xylostella

```{r}

P26 <- ggplot(PPR1, aes(amendment1, survival))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Survival of Plutella xylostella larvae (%)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P26 + ylim (0, 100)

ggsave("boxplot_P26.pdf", width = 5, height = 4, dpi = 1000)# P26 = Figure 5 in the manuscript


P27<- ggplot(PPR2, aes(amendment2, survival))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Survival of Plutella xylostella larvae (%)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P27 + ylim (0, 80)

ggsave("boxplot_P27.jpeg", width = 5, height = 4, dpi = 1000)


# leaf damage scores
P28 <- ggplot(PLD1, aes(amendment1, score1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf feeding damage score (1-7)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P28 + ylim (0, 7)

ggsave("boxplot_P28.jpeg", width = 5, height = 4, dpi = 1000)


P29 <- ggplot(PLD2, aes(amendment2, score2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf feeding damage score (1-7)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P29 + ylim (0, 7)

ggsave("boxplot_P29.jpeg", width = 5, height = 4, dpi = 1000)

```



