---
title: "Plant Growth Indices"
author: "S.Y. CHIA"
date: "January 16 2023"
output:
pdf_document: default
html_document: default
editor_options: null
chunk_output_type: console
---

# Load required R libraries

```{r}

library(ggplot2)
library(car)
library(agricolae)
library(ggpubr)
library(emmeans)
library(multcompView)
library(plotrix) # for bar plots
library(lme4)
library(tidyverse)
library(RColorBrewer)
library(GGally)
library(lattice)
library(ggthemes)
library(DHARMa)
library(rmarkdown)
library(dgof)
library(moments)
library(glmmTMB)
library(dplyr)

```

# Set working directory

```{r}
setwd("C:/ATP_PROJECT/Data")
```

# Load and prepare the data

```{r}

LA1<-read.table("Leafarea_trial_1.txt",header=TRUE)
LA2<-read.table("Leafarea_trial_2.txt",header=TRUE)
LN1<-read.table("Number_of_leaves_trial_1.txt",header=TRUE)
LN2<-read.table("Number_of_leaves_trial_2.txt",header=TRUE)
FT1<-read.table("flowering_time_trial_1.txt",header=TRUE)
FT2<-read.table("flowering_time_trial_2.txt",header=TRUE)

LA_N_incu<-read.table("IncubatedFrass_leafarea_leafcount.txt",header=TRUE)
LA_N_comp<-read.table("CompostedFrass_leafarea_leafcount.txt",header=TRUE)
FT_incu<-read.table("IncubatedFrass_floweringtime.txt",header=TRUE)
FT_comp<-read.table("CompostedFrass_floweringtime.txt",header=TRUE)


```

# Save data in appropriate format: 
#### Set the variable characteristics correctly for LA1, LA2, LN1, LN2

```{r}

# Raw frass
LA1$amendment1 <- as.factor(LA1$amendment1)
LA1$time1 <- as.factor(LA1$time1) 
LA1$plant_id1 <- as.factor(LA1$plant_id1)
LA1$trial1 <- as.factor(LA1$trial1)
LA1$leafarea1 <- as.numeric(LA1$leafarea1)
LA1$leaflength1 <- as.numeric(LA1$leaflength1)
LA1$leafwidth1 <- as.numeric(LA1$leafwidth1)
	
LA2$amendment2 <- as.factor(LA2$amendment2)
LA2$time2 <- as.factor(LA2$time2) 
LA2$plant_id2 <- as.factor(LA2$plant_id2)
LA2$trial2 <- as.factor(LA2$trial2)
LA2$leafarea2 <- as.numeric(LA2$leafarea2)
LA2$leaflength2 <- as.numeric(LA2$leaflength2)
LA2$leafwidth2 <- as.numeric(LA2$leafwidth2)

LN1$amendment1 <- as.factor(LN1$amendment1)
LN1$time1 <- as.factor(LN1$time1)
LN1$trial1 <- as.factor(LN1$trial1) 
LN1$plant_id1 <- as.factor(LN1$plant_id1)
LN1$no_leaves1 <- as.numeric(LN1$no_leaves1)

LN2$amendment2 <- as.factor(LN2$amendment2)
LN2$time2 <- as.factor(LN2$time2)
LN2$trial2 <- as.factor(LN2$trial2) 
LN2$plant_id2 <- as.factor(LN2$plant_id2)
LN2$no_leaves2 <- as.numeric(LN2$no_leaves2)

FT1$amendment1 <- as.factor(FT1$amendment1)
FT1$trial1 <- as.factor(FT1$trial1) 
FT1$plant_id1 <- as.factor(FT1$plant_id1)
FT1$days_1 <- as.numeric(FT1$days_1)

FT2$amendment2 <- as.factor(FT2$amendment2)
FT2$trial2 <- as.factor(FT2$trial2) 
FT2$plant_id2 <- as.factor(FT2$plant_id2)
FT2$days_2 <- as.numeric(FT2$days_2)


# pre-treated (incubated and composted) frass

LA_N_incu$amendment<- as.factor(LA_N_incu$amendment)
LA_N_incu$time<- as.factor(LA_N_incu$time)
LA_N_incu$plant_id<- as.factor(LA_N_incu$plant_id)
LA_N_incu$leaf_count<- as.numeric(LA_N_incu$leaf_count)
LA_N_incu$leafarea<- as.numeric(LA_N_incu$leafarea)

LA_N_comp$amendment<- as.factor(LA_N_comp$amendment)
LA_N_comp$time <-as.factor(LA_N_comp$time)
LA_N_comp$plant_id<- as.factor(LA_N_comp$plant_id)
LA_N_comp$leaf_count<- as.numeric(LA_N_comp$leaf_count)
LA_N_comp$leafarea<- as.numeric(LA_N_comp$leafarea)

FT_incu_comp$amendment<- as.factor(FT_incu_comp$amendment)
FT_incu_comp$Incubated<- as.numeric(FT_incu_comp$Incubated)
FT_incu_comp$Composted<- as.numeric(FT_incu_comp$Composted)

FT_incu$amendment<- as.factor(FT_incu$amendment)
FT_incu$days_incu<- as.numeric(FT_incu$days_incu)

FT_comp$amendment<- as.factor(FT_comp$amendment)
FT_comp$days_comp<- as.numeric(FT_comp$days_comp)
```

# View data structure and summary stats

```{r}

str(LA1)
summary(LA1)

str(LA2)
summary(LA2)

str(LN1)
summary(LN1)

str(LN2)
summary(LN2)

str(FT1)
summary(FT1)

str(FT2)
summary(FT2)

str(LA_N_incu)
summary(LA_N_incu)

str(LA_N_comp)
summary(LA_N_comp)

str(FT_incu_comp)
summary(FT_incu_comp)

str(FT_incu)
summary(FT_incu)

str(FT_comp)
summary(FT_comp)

```

# Visualize data - Leaf Area (LA)

Using boxplots, Q-Q Plots, bar graphs
'QQ Plot stands for Quantile vs Quantile Plot, which is exactly what it does: plotting theoretical quantiles against the actual quantiles of our variable'.
   
**sample sizes are very large (>30), therefore I ignore the test for normality**

```{r}

#leaf area and leaf count, raw frass
P <- ggplot(data = LA1, aes(x = amendment1, y = leafarea1))
    P + geom_boxplot()
    P + geom_col()
ggplot(data = LA1, aes(x = amendment1, y = leafarea1)) + geom_point()

qqnorm(LA1$leafarea1, pch = 1, frame = FALSE)
qqline(LA1$leafarea1, col = "steelblue", lwd = 2)


P1 <- ggplot(data = LA2, aes(x = amendment2, y = leafarea2))
    P1 + geom_boxplot()
    P1 + geom_col()
ggplot(data = LA2, aes(x = amendment2, y = leafarea2)) + geom_point()

qqnorm(LA2$leafarea2, pch = 1, frame = FALSE)
qqline(LA2$leafarea2, col = "steelblue", lwd = 2)


```

# Visualize data -Number of leaves (LN):

**sample sizes are very large (>30), therefore I ignore the test for normality**

```{r}

#leaf area and leaf count, raw frass
P2 <- ggplot(data = LN1, aes(x = amendment1, y = no_leaves1))
    P2 + geom_boxplot()
    P2 + geom_col()
ggplot(data = LN1, aes(x = amendment1, y = no_leaves1)) + geom_point()


P3 <- ggplot(data = LN2, aes(x = amendment2, y = no_leaves2))
    P3 + geom_boxplot()
    P3 + geom_col()

ggplot(data = LN1, aes(x = amendment1, y = no_leaves1)) + geom_point()
ggplot(data = LN2, aes(x = amendment2, y = no_leaves2)) + geom_point()

qqnorm(LN1$no_leaves1, pch = 1, frame = FALSE)
qqline(LN2$no_leaves2, col = "steelblue", lwd = 2)


#leaf area and leaf count, incubated frass
Pa3 <- ggplot(data = LA_N_incu, aes(x = amendment, y = leafarea))
    Pa3 + geom_boxplot()
    Pa3 + geom_col()
ggplot(data = LA_N_incu, aes(x = amendment, y = leafarea)) + geom_point()

Pb3 <- ggplot(data = LA_N_incu, aes(x = amendment, y = leaf_count))
    Pb3 + geom_boxplot()
    Pb3 + geom_col()
ggplot(data = LA_N_incu, aes(x = amendment, y = leaf_count)) + geom_point()


#leaf area and leaf count, composted frass
Pc3 <- ggplot(data = LA_N_comp, aes(x = amendment, y = leafarea))
    Pc3 + geom_boxplot()
    Pc3 + geom_col()
ggplot(data = LA_N_comp, aes(x = amendment, y = leafarea)) + geom_point()

Pd3 <- ggplot(data = LA_N_comp, aes(x = amendment, y = leaf_count))
    Pd3 + geom_boxplot()
    Pd3 + geom_col()
ggplot(data = LA_N_comp, aes(x = amendment, y = leaf_count)) + geom_point()

```

# Visualize data -Flowering time (FT):

```{r}

#flowering time, raw frass
P3a <- ggplot(data = FT1, aes(x = amendment1, y = days_1))
    P3a + geom_boxplot()
    P3a + geom_col()
ggplot(data = FT1, aes(x = amendment1, y = days_1)) + geom_point()


P3b <- ggplot(data = FT2, aes(x = amendment2, y = days_2))
    P3b + geom_boxplot()
    P3b + geom_col()
ggplot(data = FT2, aes(x = amendment2, y = days_2)) + geom_point()


#flowering time, processed frass (incubated and composted frass)
Pd3 <- ggplot(data = FT_incu_comp, aes(x = amendment, y = Incubated))
    Pd3 + geom_boxplot()
    Pd3 + geom_col()
ggplot(data = FT_incu_comp, aes(x = amendment, y = Incubated)) + geom_point()

Pe3 <- ggplot(data = FT_incu_comp, aes(x = amendment, y = Composted))
    Pe3 + geom_boxplot()
    Pe3 + geom_col()
ggplot(data = FT_incu_comp, aes(x = amendment, y = Composted)) + geom_point()


```

# Test for homogeneity of variance - Leaf Area (LA)

**If the p-value for the 'Levene test' is greater than . 05, then the variances are not significantly different from each other (i.e., the homogeneity assumption of the variance is met).**

**If the p-value for the Levene's test is less than . 05, then there is a Significant difference between the variances.**

```{r}

leveneTest(leafarea1 ~ amendment1, data = LA1)
fligner.test(leafarea1 ~ amendment1, data = LA1)
bartlett.test(leafarea1 ~ amendment1, data = LA1) 

leveneTest(leafarea2 ~ amendment2, data = LA2)
fligner.test(leafarea2 ~ amendment2, data = LA2)
bartlett.test(leafarea2~ amendment2, data = LA2) 

```

## Homogeneity - Number of leaves (LN)

```{r}
leveneTest(no_leaves1 ~ amendment1, data = LN1)
fligner.test(no_leaves1 ~ amendment1, data = LN1)
bartlett.test(no_leaves1 ~ amendment1, data = LN1)

leveneTest(no_leaves2 ~ amendment2, data = LN2)
fligner.test(no_leaves2 ~ amendment2, data = LN2)
bartlett.test(no_leaves2 ~ amendment2, data = LN2) 

```

# Test for Normality of variances - Leaf Area, Number of leaves

**If the sample size is large enough (n > 30), we can ignore the distribution of the data and use parametric tests. The central limit theorem tells us that no matter what distribution things have, 
the sampling distribution tends to be normal if the sample is large enough (n > 30).

*Shapiro-Wilk test* (recommended by Ghasemi & Zahediasl, 2002, doi: 10.5812/ijem.3505). It provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores.

**If the p-value is less than or equal to the significance level, the decision is to reject the null hypothesis and conclude that your data do not follow a normal distribution**.

```{r}

shapiro.test(LA1$leafarea1)
shapiro.test(LA2$leafarea2)

shapiro.test(LN1$no_leaves1)
shapiro.test(LN2$no_leaves2)

```

#  Model seection

```{r}
#leaf area, raw frass
lmer.LA1 <- lmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LA1)
glmmTMB.LA1 <- glmmTMB(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LA1)
gamma.LA1 <- glmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LA1)
AIC(lmer.LA1, glmmTMB.LA1, gamma.LA1)

lmer.LA2 <- lmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LA2)
glmmTMB.LA2 <- glmmTMB(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LA2)
gamma.LA2 <- glmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LA2)
AIC(lmer.LA2, glmmTMB.LA2, gamma.LA2)

# leaf count, raw frass
lmer.LN1 <- lmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LN1)
glmmTMB.LN1 <- glmmTMB(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LN1)
gamma.LN1 <- glmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LN1)
AIC(lmer.LN1, glmmTMB.LN1, gamma.LN1)

lmer.LN2 <- lmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LN2)
glmmTMB.LN2 <- glmmTMB(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LN2)
gamma.LN2 <- glmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LN2)
AIC(lmer.LN2, glmmTMB.LN2, gamma.LN2)

#leaf area, processed frass
lmer.LA_N_incu <- lmer(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
glmmTMB.LA_N_incu <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
gamma.LA_N_incu <- glmer(leafarea ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_incu)
AIC(lmer.LA_N_incu, glmmTMB.LA_N_incu, gamma.LA_N_incu)

lmer.LA_N_comp <- lmer(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
glmmTMB.LA_N_comp <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
gamma.LA_N_comp  <- glmer(leafarea ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_comp)
AIC(lmer.LA_N_comp , glmmTMB.LA_N_comp, gamma.LA_N_comp)

#leaf count, processed frass
pois.LA_N_incuL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = poisson, data = LA_N_incu)
glmmTMB.LA_N_incuL <- glmmTMB(leaf_count ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
gamma.LA_N_incuL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_incu)
AIC(pois.LA_N_incuL, glmmTMB.LA_N_incuL, gamma.LA_N_incuL)

pois.LA_N_compL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = poisson, data = LA_N_comp)
glmmTMB.LA_N_compL <- glmmTMB(leaf_count ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
gamma.LA_N_compL <-glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_comp)
AIC(pois.LA_N_compL, glmmTMB.LA_N_compL, gamma.LA_N_compL)

# flowering time, raw frass
pois.FT1 <- glm(days_1 ~ amendment1, data = FT1, family = poisson)
pois.FT1 <- glm(days_1 ~ amendment1, data = FT1, family = poisson)

glm.FT1 <- glm(days_1 ~ amendment1, data = FT1)
gamma.FT1 <- glm(days_1 ~ amendment1, family = Gamma(link = "log"), data = FT1)
AIC(pois.FT1, glm.FT1, gamma.FT1)

pois.FT2 <- glm(days_2 ~ amendment2, data = FT2, family = poisson)
glm.FT2 <- glm(days_2 ~ amendment2, data = FT2)
gamma.FT2 <- glm(days_2 ~ amendment2, family = Gamma(link = "log"), data = FT2)
AIC(pois.FT2, glm.FT2, gamma.FT2)


#flowering time, processed frass
pois.FT_incu <- glm(days_incu ~ amendment, data = FT_incu, family = poisson)
gamma.FT_incu <- glm(days_incu ~ amendment, family = Gamma(link = "log"), data = FT_incu)
AIC(pois.FT_incu, gamma.FT_incu)

pois.FT_comp <- glm(days_comp ~ amendment, data = FT_comp, family = poisson)
gamma.FT_comp <- glm(days_comp ~ amendment, family = Gamma(link = "log"), data = FT_comp)
AIC(pois.FT_comp, gamma.FT_comp)


#check for model problems using the DHARMa package - no problems detected
simulationOutput <- simulateResiduals(fittedModel = pois.FT_incu)
plot(simulationOutput)

simulationOutputinc <- simulateResiduals(fittedModel = gamma.FT_incu)
plot(simulationOutputinc)

simulationOutput <- simulateResiduals(fittedModel = pois.FT_comp)
plot(simulationOutput)

simulationOutput <- simulateResiduals(fittedModel = gamma.FT_comp)
plot(simulationOutput)

```

# Data analysis - Leaf Area, Number of leaves, flowering time

**Fit a mixed model: amendment effect is fixed, time and plant_id are random and independent.**
**effect of soil amendment was significant on leaf area and number of leaves**

```{r}

gamma.LA1 <- glmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LA1)
Anova(gamma.LA1)

gamma.LA2 <- glmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LA2)
Anova(gamma.LA2)

gamma.LN1 <- glmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"), data = LN1)
Anova(gamma.LN1)

gamma.LN2 <- glmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LN2)
Anova(gamma.LN2)

pois.FT1 <- glm.nb(days_1 ~ amendment1, data = FT1, family = poisson)
Anova(pois.FT1) # significant, but post hoc test is not!

pois.FT2 <- glm(days_2 ~ amendment2, data = FT2, family = poisson)
Anova(pois.FT2)

#Processed frass
glmmTMB.LA_N_incu <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_incu)
Anova(glmmTMB.LA_N_incu)
glmmTMB.LA_N_comp <- glmmTMB(leafarea ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
Anova(glmmTMB.LA_N_comp)
gamma.LA_N_incuL <- glmer(leaf_count ~ amendment + (1|time) + (1|plant_id), family = Gamma(link = "log"), data = LA_N_incu)
Anova(gamma.LA_N_incuL)
glmmTMB.LA_N_compL <- glmmTMB(leaf_count ~ amendment + (1|time) + (1|plant_id), data = LA_N_comp)
Anova(glmmTMB.LA_N_compL)
pois.FT_incu <- glm(days_incu ~ amendment, data = FT_incu, family = poisson)
Anova(pois.FT_incu)
pois.FT_comp <- glm(days_comp ~ amendment, data = FT_comp, family = poisson)
Anova(pois.FT_comp)

```

# Posthoc test

**Tukey test using the emmeans (estimated marginal means) package**

```{r}
#raw frass
HSD_test <- emmeans(ref_grid(gamma.LA1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(gamma.LA1, regrid = "response"), pairwise ~ amendment1) 

HSD_test <- emmeans(ref_grid(gamma.LA2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(gamma.LA2, regrid = "response"), pairwise ~ amendment2)

HSD_test <- emmeans(ref_grid(gamma.LN1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(gamma.LN1, regrid = "response"), pairwise ~ amendment1)

HSD_test <- emmeans(ref_grid(gamma.LN2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(gamma.LN2, regrid = "response"), pairwise ~ amendment2)

HSD_test <- emmeans(ref_grid(pois.FT1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(pois.FT1, regrid = "response"), pairwise ~ amendment1) # glm is sig. but post hoc test is not sig.!



#processed frass
HSD_test <- emmeans(ref_grid(glmmTMB.LA_N_incu, regrid = "response"), pairwise ~ amendment)
emmeans(ref_grid(glmmTMB.LA_N_incu, regrid = "response"), pairwise ~ amendment)

HSD_test <- emmeans(ref_grid(glmmTMB.LA_N_comp, regrid = "response"), pairwise ~ amendment)
emmeans(ref_grid(glmmTMB.LA_N_comp, regrid = "response"), pairwise ~ amendment)

HSD_test <- emmeans(ref_grid(gamma.LA_N_compL, regrid = "response"), pairwise ~ amendment)
emmeans(ref_grid(gamma.LA_N_compL, regrid = "response"), pairwise ~ amendment) 


```

# Plots for leafarea, Number of leaves

```{r, echo=TRUE, eval=TRUE}

P4 <- ggplot(LA1, aes(amendment1, leafarea1))+ 
  geom_boxplot(aes(fill = amendment1),show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6")) # Dark Sky Blue
P4 + ylim(0, 115)

ggsave("boxplot_P4.jpeg", width = 5, height = 4, dpi = 1000)


P5 <- ggplot(LA2, aes(amendment2, leafarea2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6")) # Dark Sky Blue
P5 + ylim(0, 115)

ggsave("boxplot_P5.jpeg", width = 5, height = 4, dpi = 1000)


P6 <- ggplot(LN1, aes(amendment1, no_leaves1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P6 + ylim(0, 15)

ggsave("boxplot_P6.jpeg", width = 5, height = 4, dpi = 1000)


P7 <- ggplot(LN2, aes(amendment2, no_leaves2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P7 + ylim(0, 15)

ggsave("boxplot_P7.jpeg", width = 5, height = 4, dpi = 1000)


P7a <- ggplot(FT1, aes(amendment1, days_1))+ 
  geom_boxplot(aes(fill = amendment1), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + # repeating this line helps to make the "mean symbol appear pure white
  labs(x = "Treatment", y = "Flowering time (days)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P7a + ylim (0, 96)

ggsave("boxplot_P7a.jpeg", width = 5, height = 4, dpi = 1000)


P7b <- ggplot(FT2, aes(amendment2, days_2))+ 
  geom_boxplot(aes(fill = amendment2), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + # repeating this line helps to make the "mean symbol appear pure white
  labs(x = "Treatment", y = "Flowering time (days)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P7b + ylim (0, 80)

ggsave("boxplot_P7b.jpeg", width = 5, height = 4, dpi = 1000)


#Processed frass - plots

P8a <- ggplot(LA_N_incu, aes(amendment, leafarea))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8a + ylim(0, 60)

ggsave("boxplot_P8a.jpeg", width = 5, height = 4, dpi = 1000)

P8b <- ggplot(LA_N_comp, aes(amendment, leafarea))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Leaf area (sq cm)")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8b + ylim(0, 60)

ggsave("boxplot_P8b.jpeg", width = 5, height = 4, dpi = 1000)


P8c <- ggplot(LA_N_incu, aes(amendment, leaf_count))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8c + ylim(0, 15)

ggsave("boxplot_P8c.jpeg", width = 5, height = 4, dpi = 1000)


P8d <- ggplot(LA_N_comp, aes(amendment, leaf_count))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Number of leaves")+
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8d + ylim(0, 16)

ggsave("boxplot_P8d.jpeg", width = 5, height = 4, dpi = 1000)


P8e <- ggplot(FT_incu, aes(amendment, days_incu))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Flowering time (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8e + ylim(0, 60)

ggsave("boxplot_P8e.jpeg", width = 5, height = 4, dpi = 1000)


P8f <- ggplot(FT_comp, aes(amendment, days_comp))+ 
  geom_boxplot(aes(fill = amendment), show.legend = FALSE) + 
  stat_summary(fun = mean, geom = "point", col = "white", shape = 12) +
  stat_summary(fun = mean, geom = "point", col = "white") + 
  labs(x = "Treatment", y = "Flowering time (days)") +
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P8f + ylim(0, 60)

ggsave("boxplot_P8f.jpeg", width = 5, height = 4, dpi = 1000)


```


```{r}


```
