---
title: "Plant Growth Indices"
author: "S.Y. CHIA"
date: "January 16 2023"
output:
pdf_document: default
html_document: default
editor_options: null
chunk_output_type: console
---

# Load required R libraries

```{r}

library(ggplot2)
library(car)
library(agricolae)
library(ggpubr)
library(emmeans)
library(multcompView)
library(plotrix) # for bar plots
library(lme4)
library(tidyverse)
library(RColorBrewer)
library(GGally)
library(lattice)
library(ggthemes)
library(DHARMa)
library(rmarkdown)
library(dgof)
library(moments)
library(glmmTMB)
library(dplyr)

```

# Set working directory

```{r}
setwd("C:/ATP_PROJECT/Data")
```

# Load and prepare the data

## Read in LEAF AREA data - trial 1
## Read in LEAF AREA data - trial 2

## Read in LEAF NUMBER data - trial 1
## Read in LEAF NUMBER data - trial 2
```{r}

LA1<-read.table("Leafarea_trial_1.txt",header=TRUE)
LA2<-read.table("Leafarea_trial_2.txt",header=TRUE)
LN1<-read.table("Number_of_leaves_trial_1.txt",header=TRUE)
LN2<-read.table("Number_of_leaves_trial_2.txt",header=TRUE)

```

# Save data in appropriate format: 
## Set the variable characteristics correctly for LA1, LA2, LN1, LN2
### specify factor and numeric variables

```{r}

LA1$amendment1 <- as.factor(LA1$amendment1)
LA1$time1 <- as.factor(LA1$time1) 
LA1$plant_id1 <- as.factor(LA1$plant_id1)
LA1$trial1 <- as.factor(LA1$trial1)
LA1$leafarea1 <- as.numeric(LA1$leafarea1)
LA1$leaflength1 <- as.numeric(LA1$leaflength1)
LA1$leafwidth1 <- as.numeric(LA1$leafwidth1)
	
LA2$amendment2 <- as.factor(LA2$amendment2)
LA2$time2 <- as.factor(LA2$time2) 
LA2$plant_id2 <- as.factor(LA2$plant_id2)
LA2$trial2 <- as.factor(LA2$trial2)
LA2$leafarea2 <- as.numeric(LA2$leafarea2)
LA2$leaflength2 <- as.numeric(LA2$leaflength2)
LA2$leafwidth2 <- as.numeric(LA2$leafwidth2)

LN1$amendment1 <- as.factor(LN1$amendment1)
LN1$time1 <- as.factor(LN1$time1)
LN1$trial1 <- as.factor(LN1$trial1) 
LN1$plant_id1 <- as.factor(LN1$plant_id1)
LN1$no_leaves1 <- as.numeric(LN1$no_leaves1)

LN2$amendment2 <- as.factor(LN2$amendment2)
LN2$time2 <- as.factor(LN2$time2)
LN2$trial2 <- as.factor(LN2$trial2) 
LN2$plant_id2 <- as.factor(LN2$plant_id2)
LN2$no_leaves2 <- as.numeric(LN2$no_leaves2)

```

# View data structure and summary stats

```{r}

str(LA1)
summary(LA1)

str(LA2)
summary(LA2)

str(LN1)
summary(LN1)

str(LN2)
summary(LN2)

```

# Visualize data

## Using boxplots, Q-Q Plots, bar graphs or scatter plots
   'QQ Plot stands for Quantile vs Quantile Plot, which is exactly what it does: plotting theoretical quantiles against the actual       quantiles of our variable'.
   
### Leaf Area (LA): *sample sizes are very large (>30), therefore I ignore the test for normality*

```{r, echo = TRUE, eval = TRUE}

P <- ggplot(data = LA1, aes(x = amendment1, y = leafarea1))
    P + geom_boxplot()
    P + geom_col()
ggplot(data = LA1, aes(x = amendment1, y = leafarea1)) + geom_point()

qqnorm(LA1$leafarea1, pch = 1, frame = FALSE)
qqline(LA1$leafarea1, col = "steelblue", lwd = 2)


P1 <- ggplot(data = LA2, aes(x = amendment2, y = leafarea2))
    P1 + geom_boxplot()
    P1 + geom_col()
ggplot(data = LA2, aes(x = amendment2, y = leafarea2)) + geom_point()

qqnorm(LA2$leafarea2, pch = 1, frame = FALSE)
qqline(LA2$leafarea2, col = "steelblue", lwd = 2)

```

### Number of leaves (LN): *sample sizes are very large (>30), therefore I ignore the test for normality*

```{r, echo = TRUE, eval = TRUE}

P2 <- ggplot(data = LN1, aes(x = amendment1, y = no_leaves1))
    P2 + geom_boxplot()
    P2 + geom_col()
ggplot(data = LN1, aes(x = amendment1, y = no_leaves1)) + geom_point()


P3 <- ggplot(data = LN2, aes(x = amendment2, y = no_leaves2))
    P3 + geom_boxplot()
    P3 + geom_col()

    
ggplot(data = LN1, aes(x = amendment1, y = no_leaves1)) + geom_point()
ggplot(data = LN2, aes(x = amendment2, y = no_leaves2)) + geom_point()

qqnorm(LN1$no_leaves1, pch = 1, frame = FALSE)
qqline(LN2$no_leaves2, col = "steelblue", lwd = 2)

```

# Test for homogeneity of variance
**If the p-value for the 'Levene test' is greater than . 05, then the variances are not significantly different from each other (i.e., the homogeneity assumption of the variance is met). If the p-value for the Levene's test is less than . 05, then there is a Significant difference between the variances**.
## Leaf Area (LA)

```{r, echo = FALSE, eval = FALSE}

leveneTest(leafarea1 ~ amendment1, data = LA1)
fligner.test(leafarea1 ~ amendment1, data = LA1)
bartlett.test(leafarea1 ~ amendment1, data = LA1) 

leveneTest(leafarea2 ~ amendment2, data = LA2)
fligner.test(leafarea2 ~ amendment2, data = LA2)
bartlett.test(leafarea2~ amendment2, data = LA2) 

```

## Homogeneity - Number of leaves (LN)

```{r}
leveneTest(no_leaves1 ~ amendment1, data = LN1)
fligner.test(no_leaves1 ~ amendment1, data = LN1)
bartlett.test(no_leaves1 ~ amendment1, data = LN1)

leveneTest(no_leaves2 ~ amendment2, data = LN2)
fligner.test(no_leaves2 ~ amendment2, data = LN2)
bartlett.test(no_leaves2 ~ amendment2, data = LN2) 

```

# Test for Normality of variances: 

If the sample size is large enough (n > 30), we can ignore the distribution of the data and use parametric tests. The **central limit theorem** tells us that no matter what distribution things have, 
the sampling distribution tends to be normal if the sample is large enough (n > 30).

## **Shapiro-Wilk test** (recommended by Ghasemi & Zahediasl, 2002, doi: 10.5812/ijem.3505). It provides better power than K-S. It is based on the correlation between the data and the corresponding normal scores. **If the p-value is less than or equal to the significance level, the decision is to reject the null hypothesis and conclude that your data do not follow a normal distribution**.
## Leaf Area, Leaf number

```{r}
shapiro.test(LA1$leafarea1)
shapiro.test(LA2$leafarea2)

shapiro.test(LN1$no_leaves1)
shapiro.test(LN2$no_leaves2)

```

#  Model seection

## *Gamma distribution is best based on the AIC values*

```{r}

lmer.LA1 <- lmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LA1)
glmmTMB.LA1 <- glmmTMB(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LA1)
gamma.LA1 <- glmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LA1)
AIC(lmer.LA1, glmmTMB.LA1, gamma.LA1)

lmer.LA2 <- lmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LA2)
glmmTMB.LA2 <- glmmTMB(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LA2)
gamma.LA2 <- glmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LA2)
AIC(lmer.LA2, glmmTMB.LA2, gamma.LA2)


lmer.LN1 <- lmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LN1)
glmmTMB.LN1 <- glmmTMB(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), data = LN1)
gamma.LN1 <- glmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LN1)
AIC(lmer.LN1, glmmTMB.LN1, gamma.LN1)

lmer.LN2 <- lmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LN2)
glmmTMB.LN2 <- glmmTMB(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), data = LN2)
gamma.LN2 <- glmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LN2)
AIC(lmer.LN2, glmmTMB.LN2, gamma.LN2)

```

# Data analysis

## Leaf Area  and Number of leaves data
### Fit a mixed model: amendment effect is fixed, time and plant_id are random and independent.

### Selected model *(Gamma distribution)*

#### *effect of soil amendment was significant on leaf area and number of leaves*

```{r}

gamma.LA1 <- glmer(leafarea1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"),  data = LA1)
summary(gamma.LA1)
Anova(gamma.LA1)

gamma.LA2 <- glmer(leafarea2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LA2)
summary(gamma.LA2)
Anova(gamma.LA2)


gamma.LN1 <- glmer(no_leaves1 ~ amendment1 + (1|time1) + (1|plant_id1), family = Gamma(link = "log"), data = LN1)
summary(gamma.LN1)
Anova(gamma.LN1)

gamma.LN2 <- glmer(no_leaves2 ~ amendment2 + (1|time2) + (1|plant_id2), family = Gamma(link = "log"),  data = LN2)
summary(gamma.LN2)
Anova(gamma.LN2)

```

# Posthoc test
## *Tukey test using the emmeans (estimated marginal means) package*

```{r}
HSD_test <- emmeans(ref_grid(gamma.LA1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(gamma.LA1, regrid = "response"), pairwise ~ amendment1) 

HSD_test <- emmeans(ref_grid(gamma.LA2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(gamma.LA2, regrid = "response"), pairwise ~ amendment2)

HSD_test <- emmeans(ref_grid(gamma.LN1, regrid = "response"), pairwise ~ amendment1)
emmeans(ref_grid(gamma.LN1, regrid = "response"), pairwise ~ amendment1)

HSD_test <- emmeans(ref_grid(gamma.LN2, regrid = "response"), pairwise ~ amendment2)
emmeans(ref_grid(gamma.LN2, regrid = "response"), pairwise ~ amendment2) 

```
# Plots for leafarea (cm^2) , Number of leaves

```{r, echo=TRUE, eval=TRUE}

P4 <- ggplot(LA1, aes(amendment1, leafarea1))+ 
  geom_boxplot(aes(fill = amendment1), 
  notch = FALSE, position = position_dodge(0.9), show.legend = FALSE) +
  theme_minimal() + labs(x = "Treatment", y = "Leaf area (sq cm)")+
  theme_bw() + theme(panel.grid.major = element_blank(),# removes grid background 
  panel.grid.minor = element_blank())+ 
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P4 + ylim(0, 106)

ggsave("boxplot_P4.jpeg", width = 4, height = 3, dpi = 1000)


P5 <- ggplot(LA2, aes(amendment2, leafarea2))+ 
  geom_boxplot(aes(fill = amendment2), 
  notch = FALSE, position = position_dodge(0.9), show.legend = FALSE) +
  theme_minimal() + labs(x = "Treatment", y = "Leaf area (sq cm)")+
  theme_bw() + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank())+ 
  scale_fill_manual(values = c("#BCD2E8", "#BCD2E8","#BCD2E8")) # Beau Blue
P5 + ylim(0, 104)

ggsave("boxplot_P5.jpeg", width = 4, height = 3, dpi = 1000)


P6 <- ggplot(LN1, aes(amendment1, no_leaves1))+ 
  geom_boxplot(aes(fill = amendment1), 
  notch = FALSE, position = position_dodge(0.9), show.legend = FALSE) +
  theme_minimal() + labs(x = "Treatment", y = "Number of leaves")+
  theme_bw() + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank())+ 
  scale_fill_manual(values = c("#91BAD6", "#91BAD6","#91BAD6"))# Dark Sky Blue
P6 + ylim(0, 14)

ggsave("boxplot_P6.jpeg", width = 4, height = 3, dpi = 1000)


P7 <- ggplot(LN2, aes(amendment2, no_leaves2))+ 
  geom_boxplot(aes(fill = amendment2), 
  notch = FALSE, position = position_dodge(0.9), show.legend = FALSE) +
  theme_minimal() + labs(x = "Treatment", y = "Number of leaves")+
  theme_bw() + theme(panel.grid.major = element_blank(),
  panel.grid.minor = element_blank())+ 
  scale_fill_manual(values = c("#BCD2E8", "#BCD2E8","#BCD2E8"))# Beau Blue
P7 + ylim(0, 14)

ggsave("boxplot_P7.jpeg", width = 4, height = 3, dpi = 1000)

```
# Rearrange rows

```{r}


```
